---
title: "Healthy Relationship Notebook"
params:
  council: West Central Council
output:
  html_document: default
  html_notebook: default
---

```{r hr_import_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```




```{r pre_hr&setup, echo=FALSE, warnings=FALSE, message=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

pre_hr <- dbReadTable(getRealdb,"girl_pre_1617")

hr_history <-dbReadTable(getRealdb, "basic_view")

pre_hr_1415 <-dbReadTable(getRealdb, "girl_pre_1415")

pre_hr_1314 <-dbReadTable(getRealdb, "girl_pre2013")

pre_hr_1516 <- dbReadTable(getRealdb, "girl_pre_1516")

```



```{r pre_hr_1516}

pre_hr_1516 <- pre_hr_1516 %>%
    select(council, girlCode, hr.avg) %>% #select columns of interest
    mutate("Year" = "MY-15-16") # add time frame


high_1516 <- pre_hr_1516 %>%
    filter(hr.avg >=4.45)  #find cases above 4.45


mean(pre_hr_1516$hr.avg)

nrow(high_1516)

nrow(pre_hr_1516)

achieved_1516 <- nrow(high_1516) / nrow(pre_hr_1516)  #find percent

achieved_1516 <- round(achieved_1516*100,2) #clean up percent

achieved_1516 <- paste0(achieved_1516,"%", sep="")  # add percent sign

achieved_1516




```



```{r pre_hr_1314}


pre_hr_1314 <- pre_hr_1314 %>% #start cleaning up df
    rename( council = girlScoutCouncil) %>% #rename council
    select(council, girlCode, hr_avg) %>% #select columns of interest
    mutate("Year" = "MY-13-14") # add time frame


high_1314 <- pre_hr_1314 %>%
    filter(hr_avg >=4.45)  #find cases above 4.45


achieved_1314 <- nrow(high_1314) / nrow(pre_hr_1314)  #find percent

achieved_1314 <- round(achieved_1314*100,2) #clean up percent

achieved_1314 <- paste0(achieved_1314,"%", sep="")  # add percent sign

pander(achieved_1314)  #make nice with pander

```



```{r pre_hr, echo=FALSE}
pre_hr <- pre_hr %>%
    select(council,grade, hr.avg,inProgramLastYear)

```

# Healthy Relationship Outcome 

Relationship skills are a critical component of success in all realms of life. 
The Healthy Relationship questions measures the behaviors and attitudes of the respondent regarding their relationship skills. Questions that measure healthy relationships skills include the following:


*Healthy Relationship Questions*

1. If I have a serious problem, I have people to talk with.
2. I let people know if they have hurt my feelings.
3. I let my friends know when I think they are good at something.
4. In any relationship - romantic or not - I make it clear when I don't feel comfortable.

## Pre Survey Analysis

```{r pre_num, echo=FALSE}
pre_num <- pre_hr %>%
    filter(hr.avg >=4.45)




```


The number of valid surveys entered is  `r nrow(pre_hr)`, and the number of students achieving at a high level is `r nrow(pre_num)`
and that equates to `r hr_achieved_pre()`

```{r pre_hr_hist, echo=FALSE}

pre_hr_histq <- qplot(pre_hr$hr.avg, geom="histogram", main= "Pre Survey",ylim=c(0,60), bins=40, xlab="Outcome Scores") + geom_vline(xintercept = 4.45, col="red") 

pre_hr_histq

```


# Pre Survey Healthy Relationship History


```{r}
hr_history_1 <- hr_history %>%
    select(Year, population, achieved, outcome.1, percent_achieved, mean) %>%
    filter(outcome.1 =="Healthy Relationships") %>%
    select(Year, population, percent_achieved, mean )
    
    

pander(hr_history_1)
```

