---
title: "Healthy Relationship Notebook"
output: html_notebook
params:
    council: West Central Council
---

```{r hr_import_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```


```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

pre_hr <- dbReadTable(getRealdb,"girl_pre_1617")


```

```{r}
pre_hr <- pre_hr %>%
    select(council,grade, hr.avg,inProgramLastYear)

head(pre_hr)


```







## Healthy Relationship Outcome 

Relationship skills are a critical component of success in all realms of life. 
The Healthy Relationship questions measures the behaviors and attitudes of the respondent regarding their relationship skills. Questions that measure healthy relationships skills include the following:


*Healthy Relationship Questions*

1. If I have a serious problem, I have people to talk with.
2. I let people know if they have hurt my feelings.
3. I let my friends know when I think they are good at something.
4. In any relationship - romantic or not - I make it clear when I don't feel comfortable.


````{r pre_hr_tbl}

pre_hr_table <- with(pre_hr,table(hr.avg >=4.45))

pre_hr_table

```



```{r pre_hr_function }
hr_achieved_pre()
```

