---
title: "student_survey_dm"
author: "Kevin Gilds, MPA"
date: '`r Sys.Date()`'
output: html_document
---
# Data Management

```{r}
Sys.time()
```




### Set working directory, library, and read raw data (needs updated data)


```{r}
########################Set Working Directories##################

library(tidyverse)



###########################Read 


```


### Change column names to make them human readable.
```{r}
rawdata <- readRDS("rawdata.Rds")

########################### Change Column Name #################################

colnames (rawdata)[6] <- "hr.sum"
colnames (rawdata)[7] <- "hr.avg"
colnames (rawdata)[8] <- "hr.stddev"
colnames (rawdata)[9] <- "hr.disqualify.sum"
colnames (rawdata)[10]<- "hr.disqualify.avg"
colnames (rawdata)[11]<- "hr.disqualify.std"
colnames (rawdata)[12] <- "ae.sum"
colnames (rawdata)[13] <- "ae.avg"
colnames (rawdata)[14] <- "ae.stddev"
colnames (rawdata)[15] <- "am.sum"
colnames (rawdata)[16] <- "am.avg"
colnames (rawdata)[17] <- "am.stddev"
colnames (rawdata)[18] <- "ae.disqualify.sum"
colnames (rawdata)[19] <- "ae.disqualify.avg"
colnames (rawdata)[20] <- "ae.disqualify.std"
colnames (rawdata)[21] <- "am.disqualify.sum"
colnames (rawdata)[22] <- "am.disqualify.avg"
colnames (rawdata)[23] <- "am.disqualify.std"
colnames (rawdata)[24] <- "council"
colnames (rawdata)[25] <- "girlCode"
colnames (rawdata)[26] <- "school"
colnames (rawdata)[27] <- "grade"
colnames (rawdata)[28] <- "Time"
colnames (rawdata)[29] <- "inProgramLastYear"
colnames (rawdata)[31] <- "iamMotivatedToGraduateHighSchool"
colnames (rawdata)[32] <- "iReadBooksforFun"
colnames (rawdata)[33] <- "ireallyLikeWhoIam..."
colnames (rawdata)[34] <- "..ImproveMySkilsThisYear"
colnames (rawdata)[35] <- "...UnderstandMyClassWork"
colnames (rawdata)[36] <-  "learningatSchoolIsImportantToMe"
colnames (rawdata)[37] <- "oneOfMyGoalsIstoLearn..."
colnames (rawdata)[38] <- "...WillHelpMeLaterInLife"
colnames (rawdata)[39] <- "ifIHaveASeriousProblem..."
colnames (rawdata)[40] <- "inAnyRelationshipOrNotIMakeItClear"
colnames (rawdata)[42] <- "iTalkWithMyTeachersBeforeOrAfter..."
colnames (rawdata)[43] <- "iHandinMyAssignmentsOnTime"
colnames (rawdata)[44] <- "iFinishMyHomeworkEvenIfItisBoring"
colnames (rawdata)[45] <- "ifICantUnderstandMySchoolatFirstI..."
colnames (rawdata)[46] <- "iLetPeopleKnowIfTheyHurtMyFeelings"
colnames (rawdata)[47] <- "iLetMyFriendsKnowWhenIThinkTheyAreGoodAtSomething"
colnames (rawdata)[49] <- "ILearnedFromTheBooksWeReadThisYear"
colnames (rawdata)[50] <- "myReadingSkillsImprovedThisYear"
colnames (rawdata)[51] <- "EstablishedAPostiveRelationship..."
colnames (rawdata)[52] <- "...HelpedMeRecognizeThingsIDoWell"
colnames (rawdata)[53] <- "whatDidYouLearnThisYear. "


```

### Make Student Code as class character and make all codes upper case.

```{r}

######################## Change Girl Code #################################

rawdata$girlCode <- as.character(rawdata$girlCode)

rawdata$girlCode <- toupper(rawdata$girlCode)








str(rawdata$girlCode)

dim(rawdata)

```


### Test Chunk
```{r}
###Test to see if any test girlCode in system
#rawdata$girlCode

####Test to see if any test schools in syste
#rawdata$school

###Fix if any girlCode is in Test
rawdata <- filter(rawdata, girlCode !="TEST")

council_girlCode <-with(rawdata,table(girlCode, council))

#council_girlCode

```




### Subset all finished surveys

```{r}

####################Subset Finished#####################################
# Finished 

fin <- subset (rawdata, Finished  == 1)


str(fin$girlCode)




dim(fin)


```

#Pre Surveys

### Subset Pre surveys

```{r}

############################## Subset Pre ############################3

pre <- subset (fin, Time == "Pre")
dim(pre)

```


### Subset Pre Surveys with unique student codes

```{r}

######################Find Unique Values################################################
preUnique<- pre [!(duplicated(pre$girlCode) | duplicated(pre$girlCode, fromLast = TRUE)), ]

dim(preUnique)

```


#
```{r pre_student_file_function}


pre_student_file <- function(x) {
    student_file <- filter(preUnique, council == x)
    write.csv (student_file, file="pre_student_survey.csv", row.names=FALSE)
    
    
}







```





### Subset Pre Surveys with duplicate student codes (needs updated data)
```{r}
##############################Subset duplicated girl codes##################

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

preDupes <-duplicated(pre$girlCode) | duplicated(pre$girlCode, fromLast=TRUE)

preDupes <-pre[preDupes, ]

dim(preDupes)




```

### Dupe Girl File Functions
```{r}

 

pre_student_dupe_file <- function(x) {
    pre_survey_dupes <- filter(preDupes, council == x)
    write.csv(pre_survey_dupes, "girl_survey_dupes.csv", row.names=FALSE)
}

```




# Post Survey 

### Subset post girl surveys

```{r}
##############################Subset Post###############################
post <-subset (fin, Time == "Post")


```


### Find unique student codes from post surveys
```{r}
##########################Subset Unique Post Values####################

postUnique<- post [!(duplicated(post$girlCode) | duplicated(post$girlCode, fromLast = TRUE)), ]

dim(postUnique)
```


### Find duplicate student codes from post surveys
```{r}

#########################Subset Unique Post Values######################
postDupes <-duplicated(post$girlCode) | duplicated(post$girlCode, fromLast=TRUE)

##### I think this is pulling the actuall duplicate values####################
postDupes <-post[postDupes, ]


```

### Save Data to Shiny (Web Application)
```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/Apps/girl_survey_app")

saveRDS(preUnique, file="girl_survey_03092016.rds")

```




### Send data to Sqlite database
```{r}
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

### Write Q1 Expelled data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "girl_pre_1617", value = preUnique, row.names=FALSE, overwrite=TRUE)

dbWriteTable(conn = getReal_2016db, name = "girl_pre_duplicates_1617", value = preDupes, row.names=FALSE, overwrite=TRUE)

dbWriteTable(conn = getReal_2016db, name = "girl_post_1617", value = postUnique, row.names=FALSE, overwrite=TRUE)




```

### Citrus Council
```{r make_student}

setwd("C:/Users/kevin/Dropbox/GetReal/Council_data/citrus_council")


pre_student_file("Citrus Council")

pre_student_dupe_file("Citrus Council")

```


### Gateway Council

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Council_data/gateway_council")

pre_student_file("Gateway Council")

pre_student_dupe_file("Citrus Council")



```


### Southeast Council
```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Council_data/southeast")


pre_student_file("Southeast Council")

pre_student_dupe_file("Southeast Council")


```


### Tropical Council

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Council_data/tropical_council")

pre_student_file("Tropical Council")

pre_student_dupe_file("Tropical Council")

```


### Panhandle Council

```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Council_data/panhandle_council")

pre_student_file("Panhandle Council")

pre_student_dupe_file("Panhandle Council")




```

### West Central Council

```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Council_data/west_central_council")

pre_student_file("West Central Council")


pre_student_dupe_file("West Central Council")




```
=======


```{r render_status_report}
setwd("~/GitHub/getReal20162017/Report Scripts")

rmarkdown::render("status_report.Rmd")



```

