---
title: "teacher_data_managment"
author: "Kevin Gilds"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: yes
    toc: yes
---

# Data Management Script for the Teacher Survey. 


**Data must be download from Qulatrics into a CSV file. Save the csv file into the directory below.**


## Set up R to receive the data and load the data into R. 

```{r teacher_read}
###Read Working directory

#### Required Libraries
library(dplyr)

teacher <- readRDS("teacher.Rds")


names(teacher)

```



## Make variable names easier to read

```{r teacher_variable_names}
colnames (teacher)[6] <- "council"
colnames (teacher)[7] <- "girlCode"
colnames (teacher)[8] <- "school"
colnames (teacher)[9] <- "Time"
colnames (teacher)[11] <- "graduate_ts"
colnames (teacher)[12] <- "hasConfidence"
colnames (teacher)[13] <- "goodAttitude"
colnames (teacher)[14] <- "isInterestedReading"
colnames (teacher)[15] <- "postivelyParticpates"
colnames (teacher)[16] <- "completesHomework"
colnames (teacher)[17] <- "positive_relationships"
colnames (teacher)[19] <- "helpedHerIncreasedHerSelfConfidence"
colnames (teacher)[20] <- "helpedHerAchieveSucessInSchool"
colnames (teacher)[21] <- "helpedHerDevelopPostiveRelationship"
colnames (teacher)[22] <- "benefitsFromParticipating"
colnames (teacher)[23] <- "whatCouldBeDoneToImroveTheProgram"

```


## Fix varaibles that will be trouble later

```{r test}
teacher <- filter(teacher, girlCode !="Test")
teacher <- filter(teacher, school !="Emerson")


#####Change girl code data type to character 
teacher$girlCode <- as.character(teacher$girlCode)

####Make all Girl Codes upper case
teacher$girlCode <- toupper(teacher$girlCode)


```


## Subset for finished surveys

```{r find_finished_teacher}

#####Subset Finished data entry
teacherfin <- subset (teacher, Finished == 1)




```


# Pre Survey

```{r preTeacher}

###Subset Pre Survey Values#######################3
pre_Teacher <-filter(teacherfin, Time == "Pre")


```

```{r pre_teacher_file_fun}

pre_teacher_file <- function(x) {
    pre_teacher_file <- filter(pre_Teacher, council == x)
    write.csv(pre_teacher_file, "pre_teacher.csv", row.names = FALSE)
}


```



## Find and subset unduplicated Pre cases
```{r pre_teacher_unique}

###Finds and subset uniquie Girl Code data entry
pre_teacher_unique <- preTeacher [!(duplicated(preTeacher$girlCode) | duplicated(preTeacher$girlCode, fromLast=TRUE)),]


```



```{r teacher_pre_dupes}


### Set working directory to save data to correct file folder
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Find duplicates
teacher_pre_dupes<-duplicated(preTeacher$girlCode) | duplicated(preTeacher$girlCode, fromLast=TRUE)

##### I think this is pulling the actuall duplicate values####################

teacher_pre_dupes<- preTeacher[teacher_pre_dupes,]

## How many duplicates
dim(teacher_pre_dupes)


```






# Post Survey

```{r post_teacher_unique}

#####Subset Post Survey Values#################
postTeacherUnique <- filter(teacherfin, Time == "Post")


```


## Find and subset unduplicated Post cases
```{r post_teacher_Unique}
#########################Find Unique Values Post Survey################
post_teacher_unique <-  postTeacherUnique [!(duplicated(postTeacherUnique$girlCode) | duplicated(postTeacherUnique$girlCode, fromLast=TRUE)),]

```



### Send data to Sqlite database
```{r teacher_sqllite}
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

### Write pre teacher survey  data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "pre_teacher_1617", value = pre_teacher_unique, row.names=FALSE, overwrite=TRUE)

### Write pre teacher duplicate data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "pre_teacher_dups_1617", value = teacher_pre_dupes, row.names=FALSE, overwrite=TRUE)


### Write post teacher data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "post_teacher_1617", value = postTeacherUnique, row.names=FALSE, overwrite=TRUE)




```


