---
title: "langarts_report"
author: "Kevin Gilds, MPA"
date: "May 13, 2017"
output: html_document
---

```{r lang_libraries}
library(dplyr)
library(ggplot2)
library(pander)
library(getREAL)
library(knitr)
library(formattable)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r read_lang_dat}
langarts<-readRDS("langarts.RDS")

langarts <- langarts %>%
    mutate(pt_diff = final- baseline)


dim(langarts)#test your #

```

```{r display_raw_lang}
kable(langarts)
```


```{r lang_success_fun }
success <-lang_success()
```


```{r lang_success}
lang_success <- langarts %>%
    filter(final >=2, pt_diff >=0)%>% #filter those with C and increased/maineded their grade.
    mutate("Success" = "TRUE") #add variable that they had success. 

dim(lang_success)

```


```{r lang_not_success}
lang_success_n <- langarts %>%
    filter(final >=2, pt_diff  < 0) %>% #filter those that had final higer than C but decreased grade.
    mutate("Success" = "FALSE") #add variable false

lang_success_x <- langarts %>%  #filter 
    filter(final < 2) %>%
    mutate("Success" = "FALSE")

lang_f <- rbind(lang_success_n, lang_success_x)

dim(lang_f)


```


## Counts

```{r}
increased <- langarts %>%
    filter(final >=2, pt_diff >0)





maintain <- langarts %>%
    filter(final >=2, pt_diff ==0)





#success_table <- data.frame(increased, maintain)
#kable(success_table)

fail_baseline <- langarts %>%
    filter(baseline < 2)

fail_topass <- langarts %>%
    filter(baseline < 2, final >=2)

nrow(fail_topass)



```





```{r merge_lang}
langarts <- rbind(lang_success, lang_f)

dim(langarts)
```


# Language Arts Grade Data

The number of students that were matched from a baseline grade to a final grade is **`r nrow(langarts)`**

The percent of students with a successful outcome is **`r lang_success()`**

* The number of students who increased their grade or maintained at least a C grade is **`r nrow(lang_success)`**


    * The number of students with a final grade of C and increased their grade is **`r nrow(increased)`**
    
    * The number of students who maintained at least a C grade is **`r nrow(maintain)`**


The percent of students who went from a grade of D or lower to a grade C or above is *

*   The number of students who started with a D grade or below is **`r nrow (fail_baseline)`**


*   The number of students who increased grade from a D or lower to a C grade **`r nrow(fail_topass)`**







```{r table_succes}
lang_success_1 <- langarts %>%
    count(Success) %>%
    mutate(percent = n /sum(n))
    
lang_success_1$percent <- percent(lang_success_1$percent)



kable(lang_success_1)

#g <- ggplot(lang_success_1, aes(Success = TRUE))
#g + geom_bar()

#lang_plot <-qplot(lang_success$Success==TRUE, geom="geom_col", main="Pre survey Results", xlab="Achievment at High Level")


#lang_plot

#hr_bar_pre <-qplot(hr_2016$Pre >=4.45, geom="bar", ylim=c(0, 300), main="Pre survey Results", xlab="Achievment at High Level")


```



```{r council_success}
lang_success_c <- langarts %>%
    group_by(council) %>%
    count(Success) %>%
    mutate(percent = n /sum(n))
    
lang_success_c$percent <- percent(lang_success_c$percent)

lang_success_c <- lang_success_c %>%
    filter(Success ==TRUE)


kable(lang_success_c)
```


# Grade Change

```{r mean_lang_pt}
lang_pt <- langarts %>%
    summarise(Avg =mean(pt_diff))

lang_pt
```



```{r}
langarts_change_plot2 <- ggplot(langarts,(aes(x = pt_diff, y = baseline)))

langarts_change_plot2 + geom_count() + labs (title= "Grade Change from baseline to final", x="Grade Change", y="Baseline Grade")



```

