---
title: "Academic Engagement Notebook"
params:
  council: West Central Council
output:
  github_document: default
  html_document: default
  word_document: default
---

```{r global_options_ae, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE)
```


```{r ae_import_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```




```{r pre_ae_setup, echo=FALSE, warnings=FALSE, message=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

pre_ae <- dbReadTable(getRealdb,"girl_pre_1617")

ae_history <-dbReadTable(getRealdb, "basic_view")

pre_ae_1415 <-dbReadTable(getRealdb, "girl_pre_1415")

pre_ae_1314 <-dbReadTable(getRealdb, "girl_pre2013")

pre_ae_1516 <- dbReadTable(getRealdb, "girl_pre_1516")

```
```{r pre_ae_1415, echo=FALSE}

pre_ae_1415 <- pre_ae_1415 %>%
    select(council, girlCode, ae.avg) %>% #select columns of interest
    mutate("Year" = "MY-14-15") # add time frame


high_1415 <- pre_ae_1415 %>%
    filter(ae.avg >=4.5)  #find cases above 4.5


#mean(pre_ae_1415$ae.avg)

#nrow(high_1415)

#nrow(pre_ae_1415)

achieved_1415 <- nrow(high_1415) / nrow(pre_ae_1415)  #find percent

achieved_1415 <- round(achieved_1415*100,2) #clean up percent

achieved_1415 <- paste0(achieved_1415,"%", sep="")  # add percent sign

#achieved_1415




```


```{r pre_ae_1516, echo=FALSE}

pre_ae_1516 <- pre_ae_1516 %>%
    select(council, girlCode, ae.avg) %>% #select columns of interest
    mutate("Year" = "MY-15-16") # add time frame


high_1516 <- pre_ae_1516 %>%
    filter(ae.avg >=4.5)  #find cases above 4.5


#mean(pre_ae_1516$ae.avg)

#nrow(high_1516)

#nrow(pre_ae_1516)

achieved_1516 <- nrow(high_1516) / nrow(pre_ae_1516)  #find percent

achieved_1516 <- round(achieved_1516*100,2) #clean up percent

achieved_1516 <- paste0(achieved_1516,"%", sep="")  # add percent sign

#achieved_1516




```



```{r pre_ae_1314, echo=FALSE}


pre_ae_1314 <- pre_ae_1314 %>% #start cleaning up df
    rename( council = girlScoutCouncil) %>% #rename council
    select(council, girlCode, ae_avg) %>% #select columns of interest
    mutate("Year" = "MY-13-14") # add time frame


high_1314 <- pre_ae_1314 %>%
    filter(ae_avg >=4.5)  #find cases above 4.5


achieved_1314 <- nrow(high_1314) / nrow(pre_ae_1314)  #find percent

achieved_1314 <- round(achieved_1314*100,2) #clean up percent

achieved_1314 <- paste0(achieved_1314,"%", sep="")  # add percent sign

#pander(achieved_1314)  #make nice with pander

```



```{r pre_ae, echo=FALSE}
pre_ae_inprogram <- pre_ae %>%
    select(council,grade, ae.avg,inProgramLastYear)




```

# Academic Engagement Outcome 

Academic engagement questions gauge tangible behaviors that help students succeed in school. Questions that measure academic engagement include the following.

**Acadeimc Engagement Questions**

1.	I talk with my teachers before or after school, or during lunch about my assignments.
2.	I hand in my assignments on time
3.	I finish my homework even if it is boring
4.	If I can't understand my schoolwork at first, I keep trying until I do understand it.

## Pre Survey Analysis

```{r pre_ae_num, echo=FALSE}
pre_num <- pre_ae %>%
    filter(ae.avg >=4.5) #select records with outcome score who achieved outcome at high level


pre_ae_m <- mean(pre_ae$ae.avg)

pre_ae_m <-round(pre_ae_m,2)

#pre_ae_m

```


The number of valid surveys entered is  **`r nrow(pre_ae)`**, and the number of students achieving at a high level is **`r nrow(pre_num)`**
and that equates to **`r ae_achieved_pre()`**. The average score from students is **`r pre_ae_m`**

### Academic Engagement Outcome Achievement by Council


```{r pre_council_report_ae, echo=FALSE}

pre_ae_c <-with(pre_ae,table(council, ae.avg >=4.5)) 

pre_ae_c <- prop.table(pre_ae_c, 1)


pre_ae_c <- round(pre_ae_c*100,2)
    
pander(pre_ae_c)

```


### Academic Engagement: Pre Outcome Score Summary & Council Summary

```{r pre_ae_summary, echo=FALSE}
pander(summary(pre_ae$ae.avg))

council_summary<- tapply(pre_ae$ae.avg, pre_ae$council, summary)

pander(council_summary)
```



```{r pre_ae_hist, echo=FALSE}

pre_ae_histq <- qplot(pre_ae$ae.avg, geom="histogram", main= "Pre Survey: Academic Engagment",ylim=c(0,125), bins=40, xlab="Outcome Scores") + geom_vline(xintercept = 4.5, col="red") 

pre_ae_histq

```



```{r pre_council_hist_ae}
ae_hist <- ggplot(pre_ae, aes(x=ae.avg)) 
     ae_hist + geom_histogram(fill="blue") + facet_wrap(~council) + labs(x=" All Outcome Scores", title = "Pre: Academic Engagement Scores by Council") + geom_vline(xintercept = 4.5, col="red") 



```

```{r ae_grade, echo=FALSE, eval=FALSE}
grade <- ggplot(pre_ae, aes(x=ae.avg)) 
    grade + geom_histogram(fill="blue") + facet_wrap(~grade) + labs(x=" All Outcome Scores", title = "Pre: Academic Engagement Scores by Grade Level") + geom_vline(xintercept = 4.8, col="red") 

```

```{r ae_bar, echo=FALSE}
ae_bar_pre_c <-ggplot(pre_ae, aes(hr.avg >=4.5))+ geom_bar() + facet_wrap(~council) + labs(x="Achieving at High Level", title= "Pre: Academic Engagement by Council")

ae_bar_pre_c

```


# Pre Survey: Academic Engagement History


```{r ae_histor_1, echo=FALSE}
ae_history_1 <- ae_history %>%
    select(Year, population, achieved, outcome.1, percent_achieved, mean) %>% #select variables of interest
    filter(outcome.1 =="Academic Engagement") %>% #select variable of interest
    select(Year, population, percent_achieved, mean ) # reselect variables of interest
    
    

pander(ae_history_1)
```


## Cross Validation of Academic Engagment Skills

Survey results from teachers and parents also provide useful baseline data to gauge life skills. Below are tables and graphs that provide a breakdown of questions on the pre survey from the parent and teacher surveys. 



### Pre Parent Survey


**Question 6: She works on her homework at home without supervision.** N=520




```{r parent_df_ae, echo=FALSE}

pre_parent  <- dbReadTable(getRealdb, "pre_parent_1617")

#names(pre_parent)

#post_parent <- dbReadTable(getReal_2016db, "post_parent_1617")


```




```{r ae_pre_parent, echo=FALSE}

colnames(pre_parent)[16] <- "Q6"


pre_parent_tbl <- pre_parent %>%
    select(16)

#str(pre_parent_tbl)
#str(pre_parent_tbl)
#table(pre_parent_tbl)

#names(pre_parent_tbl)

pre_parent_tbl$Q6 <- factor(pre_parent_tbl$Q6, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)



```


```{r "ae_q5_parent", fig.path='Figs/', dev.args='cario-png', echo=FALSE}

pre_parent_test <- table(pre_parent_tbl) #make tbl for testing

#nrow(pre_parent_tbl)

#pander(pre_parent_test)  #test pre parent

pre_parent_tbl_1 <- likert(pre_parent_tbl)

kable(summary(pre_parent_tbl_1))

plot(pre_parent_tbl_1)

#plot(pre_parent_tbl, type="heat") +ggtitle("Parent Pre Survey Question 6") + theme(axis.text = element_text(size = 12, colour="black"))

```

```{r pre_parent_g, fig.width=8}
pre_parent_g1 <- likert(pre_parent_tbl, grouping = pre_parent$council)

kable(summary(pre_parent_g1))

plot(pre_parent_g1)
```



### Teacher Survey

**Question 5: She positively participates in class.**  N= 360

**Question 6: She completes the homework given to her.** N= 360


```{r read_database_ae, echo=FALSE}

pre_teacher <- dbReadTable(getRealdb, "pre_teacher_1617") #read database

#names(pre_teacher)

post_teacher <- dbReadTable(getRealdb, "post_teacher_1617") #read database

```






```{r  "ae_load_teacher", fig.height=15, echo=FALSE}


#names(post_teacher) checked 

colnames(pre_teacher)[14] <- "Q5"
colnames(pre_teacher)[15] <- "Q6"

#nrow(post_teacher)

pre_teacher_tbl <- pre_teacher %>%
    select(14,15)

#str(pre_teacher_tbl)
#table(pre_teacher_tbl$Q5)
#table(pre_teacher_tbl$Q6)




pre_teacher_tbl$Q5 <- factor(pre_teacher_tbl$Q5, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly  Agree", "Agree", "Strongly Agree"),ordered = TRUE)

pre_teacher_tbl$Q6 <- factor(pre_teacher_tbl$Q6, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly  Agree", "Agree", "Strongly Agree"),ordered = TRUE)






```



```{r "ae_teacher_plots", fig.path='Figs/', dev.args='cario-png', echo=FALSE}

pre_teacher_tbl_1 <- likert(pre_teacher_tbl)

pander(summary(pre_teacher_tbl_1))

#plot(pre_teacher_tbl)

plot(pre_teacher_tbl_1)

#plot(pre_teacher_tbl, type="heat") + ggtitle("Teacher Post Survey Question 5 & 6")  + theme(axis.text = element_text(size = 12, colour="black"))



```

```{r pre_teacher_q1_g, fig.width=8}
pre_teacher_g1 <- likert(pre_teacher_tbl, grouping = pre_teacher$council)

kable(summary(pre_teacher_g1))



plot(pre_teacher_g1)
```






```{r close_ae, echo=FALSE, eval=FALSE}
close_ae <- pre_ae %>%
    filter(ae.avg >=3.5 & ae.avg <4.5)

#close_ae$ae.avg

#nrow(close_ae)
```

