---
title: "Academic Mastery Notebook"
params:
  council: West Central Council
output:
  html_document: default
  github_documet: default
  word_document: default
---

```{r global_options_am, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE)
```


```{r am_import_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```




```{r pre_am&setup, echo=FALSE, warnings=FALSE, message=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

pre_am <- dbReadTable(getRealdb,"girl_pre_1617")

am_history <-dbReadTable(getRealdb, "basic_view")

pre_am_1415 <-dbReadTable(getRealdb, "girl_pre_1415")

pre_am_1314 <-dbReadTable(getRealdb, "girl_pre2013")

pre_am_1516 <- dbReadTable(getRealdb, "girl_pre_1516")

```



```{r pre_am_1516, echo=FALSE}

pre_am_1516 <- pre_am_1516 %>%
    select(council, girlCode, am.avg) %>% #select columns of interest
    mutate("Year" = "MY-15-16") # add time frame


high_1516 <- pre_am_1516 %>%
    filter(am.avg >=4.8)  #find cases above 4.8


#mean(pre_am_1516$am.avg)

#nrow(high_1516)

#nrow(pre_am_1516)

achieved_1516 <- nrow(high_1516) / nrow(pre_am_1516)  #find percent

achieved_1516 <- round(achieved_1516*100,2) #clean up percent

achieved_1516 <- paste0(achieved_1516,"%", sep="")  # add percent sign

#achieved_1516




```


```{r pre_14_15, echo=FALSE}

pre_am_1415 <- pre_am_1415 %>%
    select(council, girlCode, am.avg) %>% #select columns of interest
    mutate("Year" = "MY-14-15") # add time frame


high_1415 <- pre_am_1415 %>%
    filter(am.avg >=4.8)  #find cases above 4.8


#mean(pre_am_1415$am.avg)

#nrow(high_1415)

#nrow(pre_am_1415)

achieved_1415 <- nrow(high_1415) / nrow(pre_am_1415)  #find percent

achieved_1415 <- round(achieved_1415*100,2) #clean up percent

achieved_1415 <- paste0(achieved_1415,"%", sep="")  # add percent sign

#achieved_1415




```



```{r pre_am_1314, echo=FALSE}


pre_am_1314 <- pre_am_1314 %>% #start cleaning up df
    rename( council = girlScoutCouncil) %>% #rename council
    select(council, girlCode, am_avg) %>% #select columns of interest
    mutate("Year" = "MY-13-14") # add time frame


high_1314 <- pre_am_1314 %>%
    filter(am_avg >=4.8)  #find cases above 4.8


achieved_1314 <- nrow(high_1314) / nrow(pre_am_1314)  #find percent

achieved_1314 <- round(achieved_1314*100,2) #clean up percent

achieved_1314 <- paste0(achieved_1314,"%", sep="")  # add percent sign

#pander(achieved_1314)  #make nice with pander

```



```{r pre_am, echo=FALSE}
pre_am <- pre_am %>%
    select(council,grade, am.avg,inProgramLastYear)

```

# Academic Mastery Outcome 



Academic mastery questions gauge a student's attitude towards school and education. Questions that measure Academic Mastery include the following.

* It's important to me that I improve my skills this year in school
* It's important to me that I really understand my class work
* Learning at school is important to me
* One of my goals in school is to learn as much as I can
* The things I am learning in school will help me later in life

## Pre Survey Analysis

```{r pre_num_am, echo=FALSE}
pre_num <- pre_am %>%
    filter(am.avg >=4.8) #select records with outcome score who achieved outcome at high level


pre_am_m <- mean(pre_am$am.avg)

pre_am_m <-round(pre_am_m,2)

#pre_am_m

```


The number of valid surveys entered is  **`r nrow(pre_am)`**, and the number of students achieving at a high level is **`r nrow(pre_num)`**
and that equates to **`r am_achieved_pre()`**. The average score from students is **`r pre_am_m`**


### Academic Mastery Outcome Achievement by Council


```{r pre_council_report_am, echo=FALSE}

pre_am_c <-with(pre_am,table(council, am.avg >=4.8)) 

pre_am_c <- prop.table(pre_am_c, 1)


pre_am_c <- round(pre_am_c*100,2)
    
pander(pre_am_c)

```


### Academic Mastery: Pre Outcome Summary & Council Summary

```{r pre_am_summary, echo=FALSE}

pander(summary(pre_am$am.avg))

council_summary<-tapply(pre_am$am.avg, pre_am$council, summary)

pander(council_summary)


```



```{r pre_am_hist, echo=FALSE}

pre_am_histq <- qplot(pre_am$am.avg, geom="histogram", main= "Pre Survey: Academic Mastery",ylim=c(0,125), bins=40, xlab="Outcome Scores") + geom_vline(xintercept = 4.8, col="red") 

pre_am_histq

```





```{r pre_council_hist_am}
am_hist_c <- ggplot(pre_am, aes(x=am.avg)) 
     am_hist_c + geom_histogram(fill="blue") + facet_wrap(~council) + labs(x=" All Outcome Scores", title = "Pre: Academic Mastery Scores by Council") + geom_vline(xintercept = 4.8, col="red") 



``` 


```{r am_grade}
grade <- ggplot(pre_am, aes(x=am.avg)) 
    grade + geom_histogram(fill="blue") + facet_wrap(~grade) + labs(x=" All Outcome Scores", title = "Pre: Academic Mastery Scores by Grade Level") + geom_vline(xintercept = 4.45, col="red") 

```




# Pre Survey: Academic Mastery History


```{r am_histor_1, echo=FALSE}
am_history_1 <- am_history %>%
    select(Year, population, achieved, outcome.1, percent_achieved, mean) %>% #select variables of interest
    filter(outcome.1 =="Academic Mastery") %>% #select variable of interest
    select(Year, population, percent_achieved, mean ) # reselect variables of interest
    
    

pander(am_history_1)
```


## Cross Validation of Academic Mastery

Survey results from teachers and parents also provide useful baseline data to gauge life skills. Below are tables and graphs that provide a breakdown of questions on the pre survey from the parent and teacher surveys. 



## Pre Parent Survey


**Question 1: She is motivated to graduate high school.** N=520

**Question 3: She has a Good Attitude About School.**  N=520



```{r parent_df_am, echo=FALSE}

pre_parent  <- dbReadTable(getRealdb, "pre_parent_1617")

#names(pre_parent)

#post_parent <- dbReadTable(getReal_2016db, "post_parent_1617")


```









```{r am_pre_survey, fig.height=5, fig.width=10, echo=FALSE}

colnames(pre_parent) [11] <- "Q1"

colnames(pre_parent) [13] <- "Q3"


pre_parent_tbl <- pre_parent %>%
    select( 11,13 )

#str(pre_parent_tbl)

#levels(pre_parent_tbl)[levels(pre_parent_tbl)=="Neither Agree/Disagree"] <- "Neutral"


pre_parent_q1 <-table(pre_parent_tbl$Q1) #make table to test

#pander(pre_parent_q1) #print results of test nicely



#pre_parent_q3 <-table(pre_parent_tbl$Q3) #make tabl to test result


#pander(pre_parent_q3) #print result of test nicely


#nrow(pre_parent_tbl) #determine total number of observations to verify percents in likert tables 



#names(pre_parent_tbl)

pre_parent_tbl$Q1 <- factor(pre_parent_tbl$Q1, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)

pre_parent_tbl$Q3 <- factor(pre_parent_tbl$Q3, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)





pre_parent_tbl_1 <- likert(pre_parent_tbl)

kable(summary(pre_parent_tbl_1))

plot(pre_parent_tbl_1)

```


```{r am_council_parent}
pre_parent_g1 <-likert(pre_parent_tbl, grouping=pre_parent$council)

kable(summary(pre_parent_g1))

plot(pre_parent_g1)
```


```{r am_pre_parent_heat,fig.width=17, echo=FALSE, eval=FALSE}
likert.heat.plot(pre_parent_tbl) + ggtitle("Pre Parent Survey Question 1 & Question 3") + theme(axis.text = element_text(size = 12, colour="black"))

```


```{r read_database_am, echo=FALSE}

pre_teacher <- dbReadTable(getRealdb, "pre_teacher_1617") #read database

#names(pre_teacher)

post_teacher <- dbReadTable(getRealdb, "post_teacher_1617") #read database

```




### Teacher Pre Survey

**Question 1: She is motivated to graduate high school.** N=360

**Question 3: She has a Good Attitude About School.** N=360


```{r am_load_pre_teacher, echo=FALSE}

colnames(pre_teacher) [11] <- "Q1"
colnames(pre_teacher) [13] <- "Q3"

pre_teacher_tbl <- pre_teacher %>%
    select(11, 13)


#nrow(pre_teacher_tbl) #total obse

pre_teacher_q1 <- table(pre_teacher_tbl$Q1) #make table to test results

#pander(pre_teacher_q1) #prints results of test



#pre_teacher_q3 <- table(pre_teacher_tbl$Q3) #make table to test 

#pander(pre_teacher_q3) #prints tests nicely



pre_teacher_tbl$Q1 <- factor(pre_teacher_tbl$Q1, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly  Agree", "Agree", "Strongly Agree"),ordered = TRUE)


pre_teacher_tbl$Q3 <- factor(pre_teacher_tbl$Q3, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly  Agree", "Agree", "Strongly Agree"),ordered = TRUE)









pre_teacher_tbl_1 <- likert(pre_teacher_tbl)

kable(summary(pre_teacher_tbl_1))

plot(pre_teacher_tbl_1)


```


```{r parent_am_council}

pre_teacher_g <- likert(pre_teacher_tbl, grouping=pre_teacher$council)

kable(summary(pre_teacher_g))

plot(pre_teacher_g)

```


```{r am_heat_pre_teacher, fig.width=17, echo=FALSE, eval=FALSE}

plot(pre_teacher_tbl, type="heat") +ggtitle("pre Teacher Survey Question 1 & Question 3") + theme(axis.text = element_text(size = 12, colour="black"))



```


### Analysis Academic Mastery

The pre survey results indicate that the students have a moderately positive attitude towards education. However, students typically come into the program with a much better attitude towards education and school. Currently just over half of the students have a positive attitude toward school whereas in the past it in mid 70's. 

Parent and teacher survey results are fairly consistent with the student surveys. Teacher survey results are more cautious in their agreement that the student has a good attitude towards education with about 55 percent in agreement. Parent surveys indicate a high level of agreement that the student has a positive attitude toward school with 80 percent in agreement. However,this is about a 10 percent decrease in level of agreement from last year. 

The academic mastery life skill will be an interesting data point to follow. If attitudes toward education changes will other life skill outcomes will improve and will academic behavior be impacted.  Currently 105 students have an outcome score that ranges from 3.8 to cutpoint from achieving the outcome at a high level. The Get REAL! program typically has not been in a position to increase this outcome. Academic Mastery is a foundation for other life skills and outcomes,  a recommendation will be to emphasize the why of education to increase motivation.



```{r close_am, echo=FALSE}
close_am <- pre_am %>%
    filter(am.avg >3.8 & am.avg <4.8)

#close_am$am.avg

#nrow(close_am)
```






