---
title: "attendance"
author: "Kevin Gilds, MPA"
date: '`r Sys.Date()`'
output:
  github_document: default
  html_document: default
bibliography: get_real.json
---
---
```{r attendance_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```


```{r attendance_db, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb <- dbConnect(SQLite(), dbname="outcome_history.sqlite")


q1_attendance <- dbReadTable(getRealdb,"Q1_attendance_1617")

```

# Decrease in Absenteeism


*Objective: 60% of participating students will either maintain or improve their attendance 
rates as demonstrated by their decreased absences from the baseline grading period to the final grading period as evidenced by report cards/school report*


```{r q1_attendance_mean, echo=FALSE}

q1_attendance$total <- as.numeric(q1_attendance$total)


```

```{r no_abs, echo=FALSE}
none_abs <- q1_attendance %>%
    filter(total ==0)

none_abs <- nrow(none_abs)/nrow(q1_attendance)

none_abs <-round(none_abs*100,2)

none_abs_p <-paste0(none_abs,"%", sep="")

#none_abs_p


```




```{r more_4, echo=FALSE}

more_4 <- q1_attendance %>% 
    filter(total >=4) #filter those with 4 or more absences into dataset

more_4 <- nrow(more_4)/nrow(q1_attendance) #obtain percent of those with more than 4 absences

more_4 <-round(more_4*100,2) #make a pretty percent

more_4_p <-paste0(more_4,"%", sep="") #make a % sign 

less_4 <-100-more_4  #obtain who has less than 4 absences 

#more_4_p

less_4_p <- paste0(less_4, "%", sep="") #provide a percent sign. 

```

The number of valid data entry records is **`r nrow(q1_attendance)`**. The percent of students without an absence is **`r (none_abs_p)`**. The percent of students with 4 or less absences is **`r (less_4_p)`** and the percent of students with more than 4 absences is **`r (more_4_p)`**. Students with more than 4 absences are at risk for chronic absenteeism if they maintain their rate of absences. 

```{r q1_absences_tbl, echo=FALSE}

q1_absences <-with(q1_attendance,table(total))  #table of absences


pander(q1_absences) #pretty table

q1_absences_c <-with(q1_attendance,table(council,total)) #table of absences by council

pander(q1_absences_c, caption= "Attendance by Council") #pretty table
```




```{r total_plot, echo=FALSE}


total_absPlot <- ggplot(q1_attendance,(aes(x =total, y = council)))

total_absPlot + geom_count()



```


### Unexcused Absences:
```{r q1_unexcused_tbl, echo=FALSE}

q1_unexcused <-with(q1_attendance,table(unexcused)) #unexcused table

pander(q1_unexcused) #pretty table

q1_unexcused_c <-with(q1_attendance,table(council, unexcused)) #unexcused table by council

pander(q1_unexcused_c, caption="Unexcused Absences by Council") #pretty table

```



### Excused Absences:
```{r excused_tbls, echo=FALSE}
q1_excused <-with(q1_attendance,table(excused)) #q1_unexucsed table

pander(q1_excused) #make pretty


q1_excused_c <-with(q1_attendance,table(council, excused)) #q1_unexcused by council

pander(q1_excused_c, caption="Excused Absences by Council") #pretty tables

```


### Attendance Analysis 

Attendance is vital for academic success and data has shown that being absent 10 percent of school days excused or unexcused places students in danger of negative outcomes such as dropping out of school[@10]. This analysis shows that a little over 20% of the students in the program are in danger of chronic absenteeism. Students with 4 or more absences in the first quarter could be labeled at risk for chronic absenteeism. 

The Get REAL! program is designed to engage at risk students and provide incentives for attendance and positive behavior. Attendance rates of students should be monitored closely to intervene as quick as possible. Last year 54% of the students improved their attendance from baseline to final grading period. 

