---
title: "attendance"
author: "Kevin Gilds, MPA"
date: '`r Sys.Date()`'
output:
  html_document: default
  github_document: default
---
```{r attendance_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```


```{r attendance_db, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb <- dbConnect(SQLite(), dbname="outcome_history.sqlite")


q1_attendance <- dbReadTable(getRealdb,"Q1_attendance_1617")

```

# Decrease in Absenteeism


*Objective: 60% of participating students will either maintain or improve their attendance 
rates as demonstrated by their decreased absences from the baseline grading period to the final grading period as evidenced by report cards/school report*


```{r q1_attendance_mean, echo=FALSE}

q1_attendance$total <- as.numeric(q1_attendance$total)


```

```{r no_abs, echo=FALSE}
none_abs <- q1_attendance %>%
    filter(total ==0)

none_abs <- nrow(none_abs)/nrow(q1_attendance)

none_abs <-round(none_abs*100,2)

none_abs_p <-paste0(none_abs,"%", sep="")

#none_abs_p


```




```{r more_4, echo=FALSE}

more_4 <- q1_attendance %>% 
    filter(total >=4) #filter those with 4 or more absences into dataset

more_4 <- nrow(more_4)/nrow(q1_attendance) #obtain percent of those with more than 4 absences

more_4 <-round(more_4*100,2) #make a pretty percent

more_4_p <-paste0(more_4,"%", sep="") #make a % sign 

less_4 <-100-more_4  #obtain who has less than 4 absences 

#more_4_p

less_4_p <- paste0(less_4, "%", sep="") #provide a percent sign. 

```

The number of valid data entry records is **`r nrow(q1_attendance)`**. The percent of students without an absence is **`r (none_abs_p)`**. The percent of students with 4 or less absences is **`r (less_4_p)`** and the percent of students with more than 4 absences is **`r (more_4_p)`**. Students with more than 4 absences are at risk for chronic absenteeism if they maintain their rate of absences. 

```{r q1_absences_tbl, echo=FALSE}

q1_absences <-with(q1_attendance,table(total))  #table of absences


pander(q1_absences) #pretty table

#q1_absences_c <-with(q1_attendance,table(council,total)) #table of absences by council

#pander(q1_absences_c) #pretty table
```




```{r total_plot, echo=FALSE}


total_absPlot <- ggplot(q1_attendance,(aes(x =total, y = council)))

total_absPlot + geom_count()



```


### Unexcused Absences:
```{r q1_unexcused_tbl, echo=FALSE}

q1_unexcused <-with(q1_attendance,table(unexcused)) #unexcused table

pander(q1_unexcused) #pretty table


#q1_unexcused_c <-with(q1_attendance,table(council, unexcused)) #unexcused table by council

#pander(q1_unexcused_c) #pretty table

```



### Excused Absences:
```{r excused_tbls, echo=FALSE}
q1_unexcused <-with(q1_attendance,table(excused)) #q1_unexucsed table

pander(q1_unexcused) #make pretty


#q1_unexcused_c <-with(q1_attendance,table(council, excused)) #q1_unexcused by council

#pander(q1_unexcused_c) #pretty tables

```


### Narrative

