---
title: "Behavior"
author: "Kevin Gilds, MPA"
date: "December 11, 2016"
output:
  github_document: default
---
```{r behavior_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```


```{r behavior_db, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb <- dbConnect(SQLite(), dbname="outcome_history.sqlite")


q1_behavior <- dbReadTable(getRealdb,"Q1_behavior_1617")

```

# Improvement in School Behavior

*Objective: 70% of participating students will show improvement in behavior by decreasing their number of suspensions from the baseline grading period to final grading period or not having a suspension during the school year as evidenced from the student's report card/school reports.*





```{r q1_attendance_mean_behavior, echo=FALSE}

q1_behavior$total <- as.numeric(q1_behavior$total)




```

```{r echo=FALSE}
no_susp <- filter(q1_behavior, total == 0)

student <- nrow(q1_behavior)

no_susp <- nrow(no_susp)

success <- no_susp/student

success <- round(success*100,2)

success <- paste0(success, "%", sep="")


    
    


```

Baseline data indicates number of valid data entries is **`r nrow(q1_behavior)`** and the percent of students who have not experienced a suspension as of Quarter 1 is **`r pander(success)`**




```{r q1_behavior_tbl, echo=FALSE}

q1_suspensions <-with(q1_behavior,table(total))  #table of absences


pander(q1_suspensions   ) #pretty table

q1_suspensions_c <- with(q1_behavior,table(council,total)) #table of absences by council

pander(q1_suspensions_c, caption="Suspensions by Council") #pretty table
```


```{r total_plot_behaivor, echo=FALSE}


total_behavior_p <- ggplot(q1_behavior,(aes(x =total, y = council)))

total_behavior_p + geom_count()



```


# Out of Scool Suspensions
```{r q1_out_tbl, echo=FALSE}

q1_out <-with(q1_behavior,table(out_school)) #unexcused table

pander(q1_out) #pretty table


q1_out_c <-with(q1_behavior,table(council, out_school)) #unexcused table by council

pander(q1_out_c, caption="Out of School Suspenions by Council") #pretty table

```



# In School Suspensions
```{r in_school_tbls}
q1_in <-with(q1_behavior,table(in_school)) #q1_unexucsed table

pander(q1_in) #make pretty


q1_in_c <-with(q1_behavior,table(council, in_school)) #q1_unexcused by council

pander(q1_in_c, caption= "In School Suspenions by Council") #pretty tables

```

# Expelled
```{r expelled, echo=FALSE}


q1_expelled <- dbReadTable(getRealdb,"Q1_expelled_1617")


q1_expelled_tbl <- with(q1_expelled,table(expelled))

pander(q1_expelled_tbl)

```



