---
title: "Healthy Relationship Notebook"
params:
  council: West Central Council
output:
  html_document: default
  github_document: default
  word_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE)
```




```{r hr_import_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```




```{r pre_hr&setup, echo=FALSE, warnings=FALSE, message=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

pre_hr <- dbReadTable(getRealdb,"girl_pre_1617")

hr_history <-dbReadTable(getRealdb, "basic_view")

pre_hr_1415 <-dbReadTable(getRealdb, "girl_pre_1415")

pre_hr_1314 <-dbReadTable(getRealdb, "girl_pre2013")

pre_hr_1516 <- dbReadTable(getRealdb, "girl_pre_1516")

```



```{r pre_hr_1516, echo=FALSE}

pre_hr_1516 <- pre_hr_1516 %>%
    select(council, girlCode, hr.avg) %>% #select columns of interest
    mutate("Year" = "MY-15-16") # add time frame


high_1516 <- pre_hr_1516 %>%
    filter(hr.avg >=4.45)  #find cases above 4.45


#mean(pre_hr_1516$hr.avg)

#nrow(high_1516)

#nrow(pre_hr_1516)

achieved_1516 <- nrow(high_1516) / nrow(pre_hr_1516)  #find percent

achieved_1516 <- round(achieved_1516*100,2) #clean up percent

achieved_1516 <- paste0(achieved_1516,"%", sep="")  # add percent sign

#achieved_1516




```



```{r pre_hr_1314, echo=FALSE}


pre_hr_1314 <- pre_hr_1314 %>% #start cleaning up df
    rename( council = girlScoutCouncil) %>% #rename council
    select(council, girlCode, hr_avg) %>% #select columns of interest
    mutate("Year" = "MY-13-14") # add time frame


high_1314 <- pre_hr_1314 %>%
    filter(hr_avg >=4.45)  #find cases above 4.45


achieved_1314 <- nrow(high_1314) / nrow(pre_hr_1314)  #find percent

achieved_1314 <- round(achieved_1314*100,2) #clean up percent

achieved_1314 <- paste0(achieved_1314,"%", sep="")  # add percent sign

#pander(achieved_1314)  #make nice with pander

```



```{r pre_hr, echo=FALSE}
pre_hr <- pre_hr %>%
    select(council,grade, hr.avg,inProgramLastYear)





```

# Healthy Relationship Outcome 

Relationship skills are a critical component of success in all realms of life. 
The healthy relationship questions measures the behaviors and attitudes of the respondent regarding their relationship skills. Questions that measure healthy relationships skills include the following:


*Healthy Relationship Questions*

1. If I have a serious problem, I have people to talk with.
2. I let people know if they have hurt my feelings.
3. I let my friends know when I think they are good at something.
4. In any relationship - romantic or not - I make it clear when I don't feel comfortable.

## Pre Survey Analysis

```{r pre_num, echo=FALSE}
pre_num <- pre_hr %>%
    filter(hr.avg >=4.45) #select records with outcome score who achieved outcome at high level


pre_hr_m <- mean(pre_hr$hr.avg)

pre_hr_m <-round(pre_hr_m,2)

#pre_hr_m

```


The number of valid surveys entered is  **`r nrow(pre_hr)`**, and the number of students achieving at a high level is **`r nrow(pre_num)`**
and that equates to **`r hr_achieved_pre()`**. The average score from students is **`r pre_hr_m`**

### Healthy Releationship: Pre Outcome Score Summary

```{r pre_hr_avg, echo=FALSE}
pander(summary(pre_hr$hr.avg))
```



```{r pre_hr_hist, echo=FALSE}

pre_hr_histq <- qplot(pre_hr$hr.avg, geom="histogram", main= "Pre Survey: Healthy Relationships",ylim=c(0,60), bins=40, xlab="Outcome Scores") + geom_vline(xintercept = 4.45, col="red") 

pre_hr_histq

```


# Pre Survey: Healthy Relationship History


```{r hr_histor_1, echo=FALSE}
hr_history_1 <- hr_history %>%
    select(Year, population, achieved, outcome.1, percent_achieved, mean) %>% #select variables of interest
    filter(outcome.1 =="Healthy Relationships") %>% #select variable of interest
    select(Year, population, percent_achieved, mean ) # reselect variables of interest
    
    

pander(hr_history_1)
```


## Cross Validation of Healthy Relationship Skills

Survey results from teachers and parents also provide useful baseline data to gauge life skills. Below are tables and graphs that provide a breakdown of questions on the pre survey from the parent and teacher surveys. 



### Pre Parent Survey





```{r parent_df, echo=FALSE}

pre_parent  <- dbReadTable(getRealdb, "pre_parent_1617")

#post_parent <- dbReadTable(getReal_2016db, "post_parent_1617")


```



**Question 5: She develops positive relationships with her classmates.** N=520



```{r pre_parent, echo=FALSE}

pre_parent_hr1 <- pre_parent %>% #select this question
    select(14)

colnames(pre_parent_hr1) [1] <- "Q5" #change name to Question 5


```



```{r pre_parent_factor, echo=FALSE}

pre_parent_hr1$Q5 <- factor(pre_parent_hr1$Q5, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE) #make factor names consistent

#str(pre_parent_hr1)

```




```{r pre_parent_tbl, echo=FALSE}

pre_parent_tbl_hr2 <- table(pre_parent_hr1) #test q5 

#nrow(pre_parent_hr1) #test to figure how total with testing %s


#pander(pre_parent_tbl) 


#class(pre_parent_hr1)
```


```{r pre_parent_likert, echo=FALSE, fig.width=17}



pre_parent_hr2 <- likert(pre_parent_hr1) #change to likert

summary(pre_parent_hr2) #test





plot(pre_parent_hr2, type="heat") + ggtitle("Pre Parent Survey Question 5") +  theme(axis.text = element_text(size = 12, colour="black"))


```


### Teacher Survey

```{r read_database, echo=FALSE}

pre_teacher <- dbReadTable(getRealdb, "pre_teacher_1617") #read database

post_teacher <- dbReadTable(getRealdb, "post_teacher_1617") #read database

```





**Question 7: She has developed positive relationships with her classmates.** N=360


```{r makeq7, echo=FALSE}

colnames(pre_teacher) [16] <- "Q7" #change name to q7 for graph

pre_teacher_tbl <- pre_teacher %>% # select variable 16 which is q7.
    select(16)


#pre_teacher_tbl_q7 <- table(pre_teacher_tbl$Q7) #test 

#pre_teacher_tbl_q7P <- prop.table(pre_teacher_tbl_q7)

#pander(pre_teacher_tbl_q7P)

#pander(pre_teacher_tbl_q7)  #test teacher post q7

#str(pre_teacher_tbl)

```









```{r factor_q7, echo=FALSE}
pre_teacher_tbl$Q7 <- factor(pre_teacher$Q7, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly  Agree", "Agree", "Strongly Agree"),ordered = TRUE)



```



```{r likert_q7, fig.width=17, echo=FALSE, fig.width=17 }
#nrow(post_teacher_tbl) #check to determine number of rows; what to divide to get %

pre_teacher_tbl <- likert(pre_teacher_tbl) #likert table


summary(pre_teacher_tbl) #likert summary



#plot(pre_teacher_tbl)

plot(pre_teacher_tbl, type="heat") + ggtitle("Pre Teacher Survey Question 7") +  theme(axis.text = element_text(size = 12, colour="black"))

```

### Healthy Relationship Analysis

The pre survey result indicates that the students in the program do not have strong relationship skills as compared to past years and this is a potential growth area for the students. Typically 61 percent of the students come into this program with strong healthy relationship skills whereas this year it was under 40 percent. 

Parent and teacher survey support the evidence from the students surveys. Nearly a quarter of parents either indicated neutral or low agreement that their child had positive relationship at school compared to 10% last years pre parent survey. Nearly 40 percent of teachers have a low or neutral agreement that the students have developed positive relationships. 

Reviewing the distribution of pre surveys scores indicates that 172 students are between 3.45 and the 4.45 cutpoint. The healthy relationship outcome skill is a strong point for the Get REAL! program as evidenced by previous years. Last year 26 percent of students improved from a low skill level to a high skill level and over 85 percent had success with this outcome.  

```{r close_hr, echo=FALSE, eval=FALSE}
close_hr <- pre_hr%>%
    filter(hr.avg >=3.45 & hr.avg < 4.45)

hist(close_hr$hr.avg)

```







