---
title: "Healthy Relationship Notebook"
params:
  council: West Central Council
output:
  html_document: default
  github_document: default
  word_document: default
---

```{r hr_import_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```




```{r pre_hr&setup, echo=FALSE, warnings=FALSE, message=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

pre_hr <- dbReadTable(getRealdb,"girl_pre_1617")

hr_history <-dbReadTable(getRealdb, "basic_view")

pre_hr_1415 <-dbReadTable(getRealdb, "girl_pre_1415")

pre_hr_1314 <-dbReadTable(getRealdb, "girl_pre2013")

pre_hr_1516 <- dbReadTable(getRealdb, "girl_pre_1516")

```



```{r pre_hr_1516, echo=FALSE}

pre_hr_1516 <- pre_hr_1516 %>%
    select(council, girlCode, hr.avg) %>% #select columns of interest
    mutate("Year" = "MY-15-16") # add time frame


high_1516 <- pre_hr_1516 %>%
    filter(hr.avg >=4.45)  #find cases above 4.45


#mean(pre_hr_1516$hr.avg)

#nrow(high_1516)

#nrow(pre_hr_1516)

achieved_1516 <- nrow(high_1516) / nrow(pre_hr_1516)  #find percent

achieved_1516 <- round(achieved_1516*100,2) #clean up percent

achieved_1516 <- paste0(achieved_1516,"%", sep="")  # add percent sign

#achieved_1516




```



```{r pre_hr_1314, echo=FALSE}


pre_hr_1314 <- pre_hr_1314 %>% #start cleaning up df
    rename( council = girlScoutCouncil) %>% #rename council
    select(council, girlCode, hr_avg) %>% #select columns of interest
    mutate("Year" = "MY-13-14") # add time frame


high_1314 <- pre_hr_1314 %>%
    filter(hr_avg >=4.45)  #find cases above 4.45


achieved_1314 <- nrow(high_1314) / nrow(pre_hr_1314)  #find percent

achieved_1314 <- round(achieved_1314*100,2) #clean up percent

achieved_1314 <- paste0(achieved_1314,"%", sep="")  # add percent sign

#pander(achieved_1314)  #make nice with pander

```



```{r pre_hr, echo=FALSE}
pre_hr <- pre_hr %>%
    select(council,grade, hr.avg,inProgramLastYear)

```

# Healthy Relationship Outcome 

Relationship skills are a critical component of success in all realms of life. 
The healthy relationship questions measures the behaviors and attitudes of the respondent regarding their relationship skills. Questions that measure healthy relationships skills include the following:


*Healthy Relationship Questions*

1. If I have a serious problem, I have people to talk with.
2. I let people know if they have hurt my feelings.
3. I let my friends know when I think they are good at something.
4. In any relationship - romantic or not - I make it clear when I don't feel comfortable.

## Pre Survey Analysis

```{r pre_num, echo=FALSE}
pre_num <- pre_hr %>%
    filter(hr.avg >=4.45) #select records with outcome score who achieved outcome at high level


pre_hr_m <- mean(pre_hr$hr.avg)

pre_hr_m <-round(pre_hr_m,2)

#pre_hr_m

```


The number of valid surveys entered is  **`r nrow(pre_hr)`**, and the number of students achieving at a high level is **`r nrow(pre_num)`**
and that equates to **`r hr_achieved_pre()`**. The average score from students is **`r pre_hr_m`**

### Healthy Releationship: Pre Outcome Score Summary

```{r pre_hr_avg, echo=FALSE}
pander(summary(pre_hr$hr.avg))
```



```{r pre_hr_hist, echo=FALSE}

pre_hr_histq <- qplot(pre_hr$hr.avg, geom="histogram", main= "Pre Survey: Health Relationships",ylim=c(0,60), bins=40, xlab="Outcome Scores") + geom_vline(xintercept = 4.45, col="red") 

pre_hr_histq

```


# Pre Survey: Healthy Relationship History


```{r hr_histor_1, echo=FALSE}
hr_history_1 <- hr_history %>%
    select(Year, population, achieved, outcome.1, percent_achieved, mean) %>% #select variables of interest
    filter(outcome.1 =="Healthy Relationships") %>% #select variable of interest
    select(Year, population, percent_achieved, mean ) # reselect variables of interest
    
    

pander(hr_history_1)
```


## Cross Validation of Healthy Relationship Skills

Survey results from teachers and parents also  Below are tables that provide a breakdown of questions on the pre survey from the parent and teacher surveys. 



### Pre Parent Survey





```{r parent_df, echo=FALSE}

pre_parent  <- dbReadTable(getRealdb, "pre_parent_1617")

#post_parent <- dbReadTable(getReal_2016db, "post_parent_1617")


```



**Question 5: She develops positive relationships with her classmates.**

Results based on responses.

```{r pre_parent, echo=FALSE}

pre_parent_hr1 <- pre_parent %>% #select this question
    select(14)

colnames(pre_parent_hr1) [1] <- "Q5" #change name to Question 5


```



```{r pre_parent_factor, echo=FALSE}

pre_parent_hr1$Q5 <- factor(pre_parent_hr1$Q5, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE) #make factor names consistent


```




```{r pre_parent_tbl, echo=FALSE}

pre_parent_tbl <- table(pre_parent_hr1) #test q5 

#nrow(pre_parent_hr1) #test to figure how total with testing %s


#pander(pre_parent_tbl) 



```


```{r pre_parent_likert, echo=FALSE, fig.width=12}

pre_parent_hr1 <- likert(pre_parent_hr1) #change to likert

summary(pre_parent_hr1) #test





plot(pre_parent_hr1, type="heat") + ggtitle("Pre Parent Survey Question 5") + theme_dark() #plot heat map


```


### Teacher Survey

```{r read_database, echo=FALSE}

pre_teacher <- dbReadTable(getRealdb, "pre_teacher_1617") #read database

post_teacher <- dbReadTable(getRealdb, "post_teacher_1617") #read database

```





**Question 7: She has developed positive relationships with her classmates.** 

Results based on number of responses. 

```{r makeq7, echo=FALSE}

colnames(pre_teacher) [16] <- "Q7" #change name to q7 for graph

pre_teacher_tbl <- pre_teacher %>% # select variable 16 which is q7.
    select(16)


pre_teacher_tbl_q7 <- table(pre_teacher_tbl$Q7) #test 

#pander(pre_teacher_tbl_q7)  #test teacher post q7

```









```{r factor_q7, echo=FALSE}
pre_teacher_tbl$Q7 <- factor(pre_teacher$Q7, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree nor Disagree", "Slightly  Agree", "Agree", "Strongly Agree"),ordered = TRUE)



```



```{r likert_q7, fig.width=15, echo=FALSE, fig.width=12 }
#nrow(post_teacher_tbl) #check to determine number of rows; what to divide to get %

pre_teacher_tbl <- likert(pre_teacher_tbl) #likert table

summary(pre_teacher_tbl) #likert summary

plot(pre_teacher_tbl)

plot(pre_teacher_tbl, type="heat") + ggtitle("Pre Teacher Survey Question 7") + theme_dark() #heat map

```

### Narrative
