---
title: "Language Arts"
author: "Kevin Gilds, MPA"
date: "December 11, 2016"
output: github_document
params: 
    council: West Central Council
    data: q1_langarts
---

# Reading Improvement
*Objective: 50% of participating students will improve their reading skills as demonstrated by their Language Arts grade increasing or maintaining a “C” grade from the baseline grading period to the final grading period as evidenced by report cards/school reports.*


```{r langarts_libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
library(getREAL)

```


```{r langarts_db, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Make connection with database
getRealdb <- dbConnect(SQLite(), dbname="outcome_history.sqlite")


q1_langarts <- dbReadTable(getRealdb,"Q1_langarts_1617")

q1_langarts1516 <-dbReadTable(getRealdb,"Q1_lang_1516")



```


```{r setup_data, echo=FALSE}


q1_16 <- q1_langarts %>%
    select(girl_code, council, langarts_course, grade, lang_pts)%>%
    mutate("Year" = "16-17")%>%
    rename(lang_avg = lang_pts)



q1_15 <- q1_langarts1516 %>%
    select(girlCode, council, langCourses, langGrade, lang_pts) %>%
    rename(girl_code =girlCode) %>%
    rename(langarts_course = langCourses)%>%
    rename(lang_avg =lang_pts)%>%
    rename(grade = langGrade) %>%
    mutate("Year" = "15-16")


lang_history <- rbind(q1_16, q1_15)


```


The number of valid data entries is **`r nrow(q1_16)`**. Students in the Get REAL! program  are off to a good to start as 98% of the students have a C or higher in Language Arts course and are doing better than last year. However, it would be advisable to monitor grades closely as students are likely to regress over the 2nd quarter. 


```{r q1_grade_table, echo=FALSE}

grade_table <- lang_history %>%
    filter(Year == "16-17")

grade_table_1 <- with(grade_table,table(Year, grade))

pander(grade_table_1, caption="Q1 Grades")

grade_table_c <-with(q1_langarts,table(council, grade))

pander(grade_table_c, caption="Q1 Grades by Council")


```

```{r courses, echo=FALSE}

q1_courses <- with(q1_langarts,table(langarts_course, grade))

pander(q1_courses, caption=" Q1:Language Arts Courses and Grades")

```


```{r grades_q1_plot, echo=FALSE}




ggplot(q1_langarts, aes(x=grade, y=langarts_course))+ geom_count()



```

```{r grade_table, echo=FALSE}

grade_table <- with(lang_history,table(Year, grade))

pander(grade_table, caption="Grade Table History--Quarter 1")


```


```{r grade_point_tbl, echo=FALSE}

grade_point <- lang_history %>%
    group_by(Year) %>%
    summarise(lang_avg = mean(lang_avg))


pander(grade_point, caption="Quarter 1 GPA History")


grade_point_c <- lang_history %>%
    group_by(council, Year)%>%
    summarize(lang_avg = mean(lang_avg))

pander(grade_point_c, caption="Quarter 1 GPA History by Council")


```












