---
title: "academic engagement"
author: "Kevin Gilds, MPA"
date: "September 29, 2016"
output: 
     github_document: default
---



```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)
library(formattable)

```


```{r read_databases, echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

ae <-dbReadTable(getReal_2016db,"ae_history")

#dim(ae)

ae_unique <- ae[!(duplicated(ae$girlCode) | duplicated(ae$girlCode, fromLast = TRUE)), ]

#dim(ae_unique)

ae_unique <- ae_unique %>% 
    mutate("Match" = "No") # Add in variable and response


ae_dupes <-duplicated(ae$girlCode) | duplicated(ae$girlCode, fromLast=TRUE) #find duplicated cases

ae_dupes <- ae[ae_dupes, ] # subset dupes

#dim(ae_dupes)

ae_dupes <- ae_dupes %>%
    mutate("Match" = "Yes") #add variable and response

ae <- rbind(ae_dupes, ae_unique)





```


```{r council_names, echo=FALSE}
## Change council names to be consistent wiht how they displayed with the surveys
ae$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, ae$council)

ae$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, ae$council)

ae$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, ae$council)

ae$council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, ae$council)

ae$council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, ae$council)

ae$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, ae$council)

ae$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, ae$council)

ae$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, ae$council)

ae$council <-sub("Girl Scouts of Gulfcoast Florida Inc.",  "Gulfcoast Council", fixed = TRUE, ae$council)

```



```{r update_yearae, echo=FALSE}
ae$Year_Id <-sub("M1",  "13-14", fixed = TRUE, ae$Year_Id)

ae$Year_Id <-sub("M2",  "14-15", fixed = TRUE, ae$Year_Id)

ae$Year_Id <-sub("M3",  "15-16", fixed = TRUE, ae$Year_Id)



```


```{r ae_succes, echo=FALSE}
ae_1 <- ae %>%
    filter(Post >=4.5)%>%
    mutate("Success" = "TRUE")

ae_2 <- ae %>%
    filter(Post <4.5)%>%
    mutate("Success" = "FALSE")

ae <- rbind(ae_1, ae_2)

head(ae)


```






# Introduction


# Data Entry Status 

```{r ae_data, echo=FALSE, eval=FALSE}
council_status <- with(ae,table(council, Year_Id))

council_status <- addmargins(council_status)


kable(council_status)

#match_status <- with(ae,table(council, Match))

#kable(match_status)



```



### Average Difference between Pre and Post Surveys

The mean difference between pre and post survey is `r pander(mean(ae$ae.diff))`. The table below shows that those in the program for multiple years did not perform better. 


```{r ae_diff, echo=FALSE}

ae_diff_m <- ae %>%
    group_by(Match) %>%
    summarise(mean= mean(ae.diff))

kable(ae_diff_m)

```






```{r ae_change_plot, echo=FALSE}
ae_change_p <- ggplot(ae,(aes(x=ae.diff, y=council)))
ae_change_p + geom_count() + geom_vline(xintercept = 0, col="red") + labs(x="Council", y="Pre Outcome Score", title="Academic Engagement Survey Results")


```

### Average Differenc by Year 
```{r year_id, echo=FALSE}
year_id_ae <- ae %>%
    group_by(Year_Id)

year_id_ae <- summarize(year_id_ae, ae.diff = mean(ae.diff))

pander(year_id_ae)

year_id_ae$Year_Id <- as.factor(year_id_ae$Year_Id)

#summary(year_id_ae)



ggplot(year_id_ae, aes(y=ae.diff, x=Year_Id, group=2)) + geom_line() + geom_point() + labs (x="Year", y= "Difference Pre and Post", title="Acedemic Engagement: Difference Pre and Post" )

```



### Average Difference between Pre and Post by Council

```{r council_ae, echo=FALSE}
council_ae <- ae %>%
    group_by(council)

council_ae_c <-summarise(council_ae, ae.diff =mean(ae.diff))

pander(council_ae_c)



```


```{r council_aey, echo=FALSE, eval=FALSE}
council_ae <- ae %>%
    group_by(council, Year_Id)

council_ae_diff <-summarise(council_ae, ae.diff =mean(ae.diff))

pander(council_ae_diff)

datatable(council_ae_diff)

```



```{r his_ae, echo=FALSE, eval=FALSE}


hist(ae$ae.diff, col="red", freq=FALSE)
ae_dent <- density(ae$ae.diff)
lines(ae_dent)

```


```{r qqnorm, echo=FALSE, eval=FALSE}

qqnorm(ae$ae.diff)
qqline(ae$ae.diff, col = 2)

```


```{r shapiro_test, echo=FALSE, eval= FALSE}
shapiro.test(ae$ae.diff)
```




```{r t_test, echo=FALSE, eval=FALSE}
t.test(ae$Pre, ae$Post)



cohen.d(ae$Pre, ae$Post)
```




##Post Survey Achievment

### By Council in Percent

```{r council_post, echo=FALSE}

council_ae <- ae %>%
    group_by(council)

achieved_ae_post <- with(council_ae, table(council, Post >= 4.5))

achieved_ae_post <-prop.table(achieved_ae_post,1)

achieved_ae_post<-round(achieved_ae_post*100,2)



kable(achieved_ae_post)

```

### Achievement by Matched Status

```{r post_ae, echo=FALSE}

match_ae <- ae %>%
    group_by(Match) %>%
    count(Post >=4.5)%>%
    mutate(percent = n /sum(n))

match_ae$percent <- percent(match_ae$percent)


kable(match_ae)
```





```{r counci_post_year, echo=FALSE, eval=FALSE}


council_ae_test <-council_ae %>%
    group_by(council,Year_Id) %>%
    count(Post >=4.5)

datatable(council_ae_test)

```



### Post Survey Average Score

The trend is that students are on averaging scoring better on the post surveys over time from the first year it was measured. However, being in the program for multiple years does not seem to increase scores compared to other students. 

```{r ae_avg_m, echo=FALSE}
ae_avg_m <- ae %>%
    group_by(Match)%>%
    summarise(Post =mean(Post))

kable(ae_avg_m)
```


```{r ae_avg, echo=FALSE}
ae_avg <- ae %>%
    group_by(Year_Id) %>%
    summarise(Post =mean(Post))

kable(ae_avg)

```

```{r plotbyyear, echo=FALSE}
ggplot(ae_avg, aes(y=Post, x=Year_Id, group=2)) + geom_line() + geom_point() + labs(x="Membership Year", y="Post Average", title="Academic Engagement: Post Survey Averages by Year")



```


### Post Survey Average Score by Council

```{r council_ae_post_tbl, echo=FALSE}


#head(council_ae)

council_ae_post <-summarise(council_ae, Post =mean(Post))

pander (council_ae_post)

```



```{r achieved_ae_pre, echo=FALSE, eval=FALSE}
achieved_ae <- with(council_ae, table(council, Pre >= 4.5))

achieved_ae

achieved_ae_p <-prop.table(achieved_ae,1)

achieved_ae_p<-round(achieved_ae_p*100,2)

pander(achieved_ae_p)
```


```{r dt_council_ae_pre, echo=FALSE, eval=FALSE}
council_ae_pre <-summarise(council_ae, Pre =mean(Pre))


datatable(council_ae_pre, rownames = FALSE)


```


