---
title: "academic engagement"
author: "Kevin Gilds, MPA"
date: "September 29, 2016"
output: html_document
---



```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)

```


```{r read_databases}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

ae <-dbReadTable(getReal_2016db,"ae_history")

dim(ae)

ae_unique <- ae[!(duplicated(ae$girlCode) | duplicated(ae$girlCode, fromLast = TRUE)), ]

dim(ae_unique)

ae_unique <- ae_unique %>% 
    mutate("Match" = "No") # Add in variable and response


ae_dupes <-duplicated(ae$girlCode) | duplicated(ae$girlCode, fromLast=TRUE) #find duplicated cases

ae_dupes <- ae[ae_dupes, ] # subset dupes

dim(ae_dupes)

ae_dupes <- ae_dupes %>%
    mutate("Match" = "Yes") #add variable and response

ae <- rbind(ae_dupes, ae_unique)





```


```{r}
## Change council names to be consistent wiht how they displayed with the surveys
ae$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, ae$council)

ae$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, ae$council)

ae$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, ae$council)

ae$council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, ae$council)

ae$council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, ae$council)

ae$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, ae$council)

ae$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, ae$council)

ae$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, ae$council)

ae$council <-sub("Girl Scouts of Gulfcoast Florida Inc.",  "Gulfcoast Council", fixed = TRUE, ae$council)

```

# Introduction

Matching survey data set from the past three membership years.

* M1 = MY: 2013-2014

* M2 = MY: 2014-2015

* M3 = MY: 2015-2016


# Data Entry Status 

```{r}
council_status <- with(ae,table(council, Year_Id))

pander(council_status)

match_status <- with(ae,table(council, Match))

pander(match_status)



```



# Academic Mastery

### General Information 

```{r ae_diff, echo=FALSE}

ae_diff_m <- ae %>%
    group_by(Match) %>%
    summarise(mean= mean(ae.diff))

kable(ae_diff_m)

```

```


The mean difference between pre and post survey is `r pander(mean(ae$ae.diff))`



```{r}
ae_change_p <- ggplot(ae,(aes(x=ae.diff, y=council)))
ae_change_p + geom_count() + geom_vline(xintercept = 0, col="red") + labs(x="Pre and Post Difference", y="Pre Outcome Score", title="Academic Engagement Survey Results")


```


```{r}
year_id_ae <- ae %>%
    group_by(Year_Id)

year_id_ae <- summarize(year_id_ae, ae.diff = mean(ae.diff))

pander(year_id_ae)

year_id_ae$Year_Id <- as.factor(year_id_ae$Year_Id)

summary(year_id_ae)



ggplot(year_id_ae, aes(y=ae.diff, x=Year_Id, group=2)) + geom_line() + geom_point()

```



### Average Difference between Pre and Post by Council

```{r}
council_ae <- ae %>%
    group_by(council)

council_ae_c <-summarise(council_ae, ae.diff =mean(ae.diff))

pander(council_ae_c)



```


### Avergage Difference between Pre and Post by Membership Year

```{r council_ae}
council_ae <- ae %>%
    group_by(council, Year_Id)

council_ae_diff <-summarise(council_ae, ae.diff =mean(ae.diff))

pander(council_ae_diff)

datatable(council_ae_diff)

```



```{r}





hist(ae$ae.diff, col="red", freq=FALSE)
ae_dent <- density(ae$ae.diff)
lines(ae_dent)



```

QNorm test
```{r}

qqnorm(ae$ae.diff)
qqline(ae$ae.diff, col = 2)

```

Shapiro Test
```{r}
shapiro.test(ae$ae.diff)
```


T-Test

```{r}
t.test(ae$Pre, ae$Post)



cohen.d(ae$Pre, ae$Post)
```




##Post Survey History

```{r post_ae, echo=FALSE}

match_ae <- ae %>%
    group_by(Match) %>%
    count(Post >=4.5)

kable(match_ae)
```

```{r}

council_ae <- ae %>%
    group_by(council)

achieved_ae_post <- with(council_ae, table(council, Post >= 4.5))

achieved_ae_post <-prop.table(achieved_ae_post,1)

achieved_ae_post<-round(achieved_ae_post*100,2)



pander(achieved_ae_post)

```



#### Post survey by Year (by Counts)
```{r}


council_ae_test <-council_ae %>%
    group_by(council,Year_Id) %>%
    count(Post >=4.5)

datatable(council_ae_test)

```



### Post Survey ae Average Score

```{r ae_avg_m}
ae_avg_m <- ae %>%
    group_by(Match)%>%
    summarise(Post =mean(Post))

kable(ae_avg_m)
```


```{r}
ae_avg <- ae %>%
    group_by(Year_Id) %>%
    summarise(Post =mean(Post))

pander(ae_avg)

```

```{r}
ggplot(ae_avg, aes(y=Post, x=Year_Id, group=2)) + geom_line() + geom_point()


```


### Post Survey Average Score by Council

```{r council_ae_post_tbl}


head(council_ae)

council_ae_post <-summarise(council_ae, Post =mean(Post))

pander (council_ae_post)

```


### Pre Surveys
```{r}
achieved_ae <- with(council_ae, table(council, Pre >= 4.5))

achieved_ae

achieved_ae_p <-prop.table(achieved_ae,1)

achieved_ae_p<-round(achieved_ae_p*100,2)

pander(achieved_ae_p)
```


```{r}
council_ae_pre <-summarise(council_ae, Pre =mean(Pre))


datatable(council_ae_pre, rownames = FALSE)


```


