---
title: "am_history"
author: "Kevin Gilds, MPA"
date: '`r Sys.Date()`'
output: 
    github_document: default
---


```{r echo=FALSE, warning=FALSE, message=FALSE}

library(formattable)
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)

```


```{r read_databases, echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

am <-dbReadTable(getReal_2016db,"am_history")

#dim(am)

am_unique<- am [!(duplicated(am$girlCode) | duplicated(am$girlCode, fromLast = TRUE)), ] #find and subset uniquie students

am_unique <- am_unique %>% 
    mutate("Match" = "No") # Add in variable and response

#dim(am_unique)

am_dupes <-duplicated(am$girlCode) | duplicated(am$girlCode, fromLast=TRUE) #find duplicated cases

am_dupes <- am[am_dupes, ] # subset dupes

#dim(am_dupes)

am_dupes <- am_dupes %>%
    mutate("Match" = "Yes") #add variable and response


am<- rbind(am_dupes, am_unique)


#dim(am)

```


```{r council_sub, echo=FALSE}
## Change council names to be consistent wiht how they displayed with the surveys
am$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, am$council)

am$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, am$council)

am$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, am$council)

am$council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, am$council)

am$council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, am$council)

am$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, am$council)

am$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, am$council)

am$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, am$council)

am$council <-sub("Girl Scouts of Gulfcoast Florida Inc.",  "Gulfcoast Council", fixed = TRUE, am$council)

```



```{r update_year, echo=FALSE}
am$Year_Id <-sub("M1",  "13-14", fixed = TRUE, am$Year_Id)

am$Year_Id <-sub("M2",  "14-15", fixed = TRUE, am$Year_Id)

am$Year_Id <-sub("M3",  "15-16", fixed = TRUE, am$Year_Id)



```




```{r succes, echo=FALSE}
am_1 <- am %>%
    filter(Post >=4.8)%>%
    mutate("Success" = "TRUE")

#dim(am_1)

am_2 <- am %>%
    filter(Post <4.8 & am.diff >0)%>%
    mutate("Success" = "TRUE")


#dim(am_2)

am_3 <- am %>%
    filter(Post < 4.8 & am.diff <=0)%>%
    mutate("Success" = "FALSE")

#dim(am_3)

am_1 <- rbind(am_1, am_2)

am <- rbind(am_1, am_3)

#head(am)

am_f <- am %>%
    filter(Success ==FALSE)

#head(am_f)
#tail(am_f)

```







```{r am_status, echo=FALSE, eval=FALSE}
council_status <- with(am,table(council, Year_Id))


council_status <- addmargins(council_status)


kable(council_status)


#match_status <- with(am,table(council, Match))

#pander(match_status)


```



# Academic Mastery


## Post Survey Achievment

```{r am_suc, echo=FALSE}
am_suc <- am %>%
    count(Success)%>%
    mutate(percent = n/sum(n))

am_suc$percent <- percent(am_suc$percent)

kable(am_suc)

```


### Achievement by Council

```{r council_am, echo=FALSE}

council_am <- am %>%
    group_by(council) %>%
    count(Success) %>%
    mutate(percent = n / sum(n))


council_am$percent <- percent(council_am$percent)

council_am <- council_am %>%
    filter(Success == TRUE)

kable(council_am)


```

### Achievment by Matched Status

```{r post_hr, echo=FALSE}
match_am <- am %>%
    group_by(Match) %>%
    count(Success) %>%
    mutate(Percent = n/sum (n))
    
match_am$Percent <- percent(match_am$Percent)

    
kable(match_am)
```








## Average Difference between Pre and Post Surveys 

The mean difference between pre and post survey is `r pander(mean(am$am.diff))`. Students who had been in the program tend to improve their attitude compared to students in the program for the first time. 


```{r an_diff_m, echo=FALSE}
am_diff_m <- am %>%
    group_by(Match) %>%
    summarise(mean= mean(am.diff))

kable(am_diff_m)

```




```{r am_plot_diff, echo=FALSE, fig.path='Figs/'}
am_change_p <- ggplot(am,(aes(x=am.diff, y=council)))
am_change_p + geom_count() + geom_vline(xintercept = 0, col="red") + labs(x="Difference Pre and Post", y="Council", title="Academic Mastery Survey Results")


```


```{r am_year_ach, echo=FALSE, fig.path='Figs/'}
year_id_am <- am %>%
    group_by(Year_Id)

year_id_am <- summarize(year_id_am, am.diff = mean(am.diff))

pander(year_id_am)

year_id_am$Year_Id <- as.factor(year_id_am$Year_Id)

#summary(year_id_am)



ggplot(year_id_am, aes(y=am.diff, x=Year_Id, group=2)) + geom_line() + geom_point() + labs (x="Year", y= "Difference Pre and Post", title="Acedemic Mastery: Difference Pre and Post" )

```



### Average Difference between Pre and Post by Council

```{r council_am_1, echo=FALSE}
council_am <- am %>%
    group_by(council)

council_am_c <-summarise(council_am, am.diff =mean(am.diff))

pander(council_am_c)



```




```{r council_am_2, echo=FALSE, eval= FALSE}
council_am <- am %>%
    group_by(council, Year_Id)

council_am_diff <-summarise(council_am, am.diff =mean(am.diff))

pander(council_am_diff)

datatable(council_am_diff)

```



```{r hist_diff, echo=FALSE, eval=FALSE}

hist(am$am.diff, col="red", freq=FALSE)
am_dent <- density(am$am.diff)
lines(am_dent)

```


```{r am_qnorm, echo=FALSE, eval=FALSE}

qqnorm(am$am.diff)
qqline(am$am.diff, col = 2)

```


```{r shapiro_test, echo=FALSE, eval=FALSE}
shapiro.test(am$am.diff)
```




```{r am_tests, echo=FALSE, eval= FALSE}
t.test(am$Pre, am$Post)



cohen.d(am$Pre, am$Post)
```




```{r am_datatable, echo=FALSE, eval=FALSE}


council_am_test <-council_am %>%
    group_by(council,Year_Id) %>%
    count(Post >=4.8)

datatable(council_am_test)

```



## Post Survey Average Scores

Overall the trend is that average scores have increased from the firs year this Academic Mastery. In year 14-15, there was a dip in the scores but in 15-16 the average score increased from 13-14. Students who have been in the program multiple year did have a have a higher average score than those who have only been in the program once. 



```{r am_avg_m, echo=FALSE}
am_avg_m <- am %>%
    group_by(Match)%>%
    summarise(Post =mean(Post))

kable(am_avg_m)
```

```{r am_avg, echo=FALSE}
am_avg <- am %>%
    group_by(Year_Id) %>%
    summarise(Post =mean(Post))

pander(am_avg)

```

```{r plot_avgs_am, echo=FALSE, fig.path='Figs/'}
ggplot(am_avg, aes(y=Post, x=Year_Id, group=2)) + geom_line() + geom_point() + labs(x="Membership Year", y="Post Average", title="Academic Mastery: Post Survey Averages by Year")



```


### Post Survey Average Score by Council

```{r council_am_post_tbl, echo=FALSE}

council_avg <- am %>%
    group_by(council)%>%
    summarise(Post =mean(Post))

kable(council_avg)


#council_am_post <-summarise(council_am, Post =mean(Post))

#pander (council_am_post)

```



```{r echo=FALSE,eval=FALSE}
achieved_am <- with(council_am, table(council, Pre >= 4.8))

achieved_am

achieved_am_p <-prop.table(achieved_am,1)

achieved_am_p<-round(achieved_am_p*100,2)

pander(achieved_am_p)
```


```{r echo=FALSE, eval=FALSE}
council_am_pre <-summarise(council_am, Pre =mean(Pre))


datatable(council_am_pre, rownames = FALSE)


```


