---
title: "Attendance_history"
author: "Kevin Gilds, MPA"
date: "February 18, 2017"
output: 
    github_document
        
---

```{r read_dbase, echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite") 

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite") #established connection with database

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)
library(formattable)
```

```{r read_1516, echo=FALSE}
attendance_1516 <-dbReadTable(getReal_2016db, "attendance_1516") #read readarts1516 table

#names(attendance_1516)

attendance_1516 <- attendance_1516 %>%
     mutate("Year_Id" = "M3")%>%
     rename(baseline = basline)%>%
     rename(Att_diff = Abs_Change)%>%
     select(1, 2, 3, 4, 6,7) #select variables of interest 
      
#names(attendance_1516)

```



```{r read_1415, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data") #change working directory to find database

getReal_2015db<- dbConnect(SQLite(),   dbname="data_Final_GetReal_2014_2015.sqlite") #read database

attendance_1415 <-dbReadTable(getReal_2015db, "absences_final") #read read_1415

#names(attendance_1415)

attendance_1415 <- attendance_1415%>% 
    mutate("Year_Id" = "M2") %>% #add variable data
    rename(Att_diff = diff)%>%
    rename(Council = council)%>%
    rename(final= total_abs_final)%>%
    rename(baseline = total_abs_baseline)%>%#rename variable/column name
    select(1,2, 4,3, 5,6)#select column of interest

#names(attendance_1415)

```

```{r attendance_his, echo=FALSE}



attendance_his <- rbind(attendance_1415, attendance_1516)



```


```{r attendance_unique, echo=FALSE }


attendance_unique <- attendance_his[!(duplicated(attendance_his$girlCode) | duplicated(attendance_his$girlCode, fromLast = TRUE)), ]

#dim(attendance_unique)

attendance_unique <- attendance_unique %>%
    mutate("Match" = "No")

#head(attendance_unique)






```

```{r attendance_dupes, echo=FALSE}

attendance_dupes <-duplicated(attendance_his$girlCode) | duplicated(attendance_his$girlCode, fromLast=TRUE)

attendance_dupes <-attendance_his[attendance_dupes, ]

#dim(susp_dupes)

attendance_dupes <- attendance_dupes %>%
    mutate("Match" = "Yes")


attendance_his <- rbind(attendance_unique, attendance_dupes)

#dim(susp_his)

#dim(attendance_his)

```




```{r council_name_fix_lang, echo=FALSE}
## Change council names to be consistent wiht how they displayed with the surveys
attendance_his$Council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, attendance_his$Council)

attendance_his$Council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, attendance_his$Council)

attendance_his$Council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, attendance_his$Council)

attendance_his$Council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, attendance_his$Council)

attendance_his$Council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, attendance_his$Council)

attendance_his$Council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, attendance_his$Council)

attendance_his$Council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, attendance_his$Council)

attendance_his$Council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, attendance_his$Council)

attendance_his$Council <-sub("Pandhandle Council", "Panhandle Council", fixed = TRUE, attendance_his$Council)


attendance_his$Council <-sub("Girl Scouts of Gulfcoast Florida Inc.",  "Gulfcoast Council", fixed = TRUE, attendance_his$Council)

```

# Introduction

Matching attendance data set from the past two membership years.

* M2 = MY: 2014-2015

* M3 = MY: 2015-2016



```{r council_stauts_lang, echo=FALSE}
council_status <- with(attendance_his,table(Council, Year_Id))



#council_status <- addmargins(council_status)

pander(council_status)

```





```{r att_dif2, echo=FALSE}
attendance_his <- attendance_his %>%
    mutate(Att_diff2 = final - baseline)


```


```{r succcess, echo=FALSE}
perfect_att <- attendance_his%>%
    filter(final ==0 & baseline ==0)%>%  #filter out students with perfect attendance
    mutate("Success" = "TRUE")


reduce_att <-attendance_his %>%
    filter(Att_diff2 < 0) %>%  #filter out students who reduced their attenance
    mutate("Success" = "TRUE")  #add success variable




attendance_his1 <-rbind(perfect_att, reduce_att)  

increase_att <- attendance_his %>%
    filter(final !=0) %>%
    filter(Att_diff2 >=0)%>%    #find students who increased their attendance and did not decreased # number of times 
    mutate("Success" = "FALSE")  #add success variable

attendance_his <- rbind(attendance_his1, increase_att)  #bind all together for analysis down the pipleline. 

attendance_suc_1 <- nrow(reduce_att) + nrow(perfect_att)

#attendance_suc_1

attendance_suc_2 <- (attendance_suc_1) / nrow(attendance_his)





attendance_suc <- percent(attendance_suc_2)


```

```{r eval=FALSE, echo=FALSE}
attendance_succ <- attendance_his %>%
    count(Success)%>%
    mutate(percent = n /sum(n))

attendance_succ

attendance_succ$n[2]

```



# Attendance Outcome Achievement

The number of students in the dataset are **`r nrow(attendance_his)`** and the number of students that could be matched across two years is **`r nrow(attendance_dupes)`**.The percent of students with a succesful outcome is **`r (attendance_suc)`**.  A successful outcome means not missing a day of school and the student decreasing their number of absences from baseline grading period to the final grading period.


```{r succ_table, echo=FALSE }
attendance_succ <- attendance_his %>%
    count(Success)%>%
    mutate(percent = n /sum(n))

attendance_succ$percent <- percent(attendance_succ$percent)



kable(attendance_succ)


```


```{r attendance_suc_match, echo=FALSE}
attendance_succ_m <- attendance_his %>%
    group_by(Match) %>%
    count(Success) %>%
    mutate(percent = n /sum(n))

attendance_succ_m$percent <- percent(attendance_succ_m$percent)

attendance_succ_m <- attendance_succ_m %>%
    filter(Success == "TRUE")

kable(attendance_succ_m)
```



### Achievment by Council

```{r attendance_succ_c, echo=FALSE}
attendance_succ_c <- attendance_his %>%
    group_by(Council, Year_Id)%>%
    count(Success)%>%
    mutate(percent = n /sum(n))
    
    
attendance_succ_c$percent <- percent(attendance_succ_c$percent)  

attendance_succ_c <- attendance_succ_c %>%
    filter(Success == "TRUE")

kable(attendance_succ_c)
    
```

### Decrease in Absences

```{r att_avg_allstudents, echo=FALSE}
attendance_avg <- attendance_his %>%
    summarise(Att_diff2 = mean(Att_diff2))

kable(attendance_avg)

```

### Average Decrease for students who had a chance to improve attendance

```{r attendance_avg1, echo=FALSE}

attendance_avg_1 <- attendance_his %>%
    filter(baseline >0 & final >0)
    
#head(attendance_avg_1)
#tail(attendance_avg_1)

attendance_avg_1 <- attendance_his %>%
    filter(baseline >0 & final >0)%>%
    summarise(Att_diff = mean(Att_diff2))


attendance_count <- attendance_his %>%
    count(Att_diff2 > 0)

#kable(attendance_count)

kable(attendance_avg_1)
```

```{r}
att_sum_m <- attendance_his %>%
    filter(baseline !=0 & final !=0) %>%
    group_by(Match) %>%
    summarise(Att_diff =mean(Att_diff2))

kable(att_sum_m)

```



```{r att_sum_year, echo=FALSE}
att_sum_y <- attendance_his %>%
    group_by(Year_Id)%>%
    summarise(Att_diff=mean(Att_diff2))

kable(att_sum_y)

```




```{r sum_att_council, echo=FALSE}
att_sum_c <- attendance_his %>%
    group_by(Council)%>%
    summarise(Att_diff2 =mean(Att_diff2))

#kable(att_sum_c)

#year_id_lang_summary <-summarise(year_id_lang_summary, Grade_Change #=mean(Grade_Change)) #summarize Grade change by year id
```
```{r abs_plot, echo=FALSE}

abs_plot <- ggplot(att_sum_c,(aes(x = Att_diff2, y =Council)))
abs_plot + geom_count()




```

