---
title: "Behavior History"
author: "Kevin Gilds, MPA"
date: "February 18, 2017"
output: 
        github_document
        
---

```{r read_dbase_beha, echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite") 

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite") #established connection with database

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)
library(formattable)

```

```{r read_1516_beh, echo=FALSE}

suspensions_1516 <-dbReadTable(getReal_2016db, "suspensions_1516") #read readarts1516 table

suspensions_1516 <- suspensions_1516 %>%
     mutate("Year_Id" = "M3")%>%
     rename(baseline = basline) %>%
     rename(council = Council) %>%
     rename(susp_diff = Suspensions_Change) %>%
     select(1,2,3,4,6,7)#select variables of interest 
      

```



```{r read_1415_beh, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data") #change working directory to find database

getReal_2015db<- dbConnect(SQLite(),   dbname="data_Final_GetReal_2014_2015.sqlite") #read database


suspenions_1415 <-dbReadTable(getReal_2015db, "behavior_data") #read read_1415



suspenions_1415 <- suspenions_1415%>% 
    mutate("Year_Id" = "M2") %>%
    rename(final = total_final)%>%
    rename(baseline = total_baseline)%>%
    rename(susp_diff = total_diff)%>%
    select(1,2,4,3,5,6)#add variable and name it M2. 

```


```{r susp_his, echo=FALSE }
#names(suspensions_1516)
#names(suspenions_1415)

susp_his <- rbind(suspensions_1516, suspenions_1415)

susp_unique<- susp_his [!(duplicated(susp_his$girlCode) | duplicated(susp_his$girlCode, fromLast = TRUE)), ]

#dim(susp_unique)

susp_unique <- susp_unique %>%
    mutate("Match" = "No")

#head(susp_unique)

susp_dupes <-duplicated(susp_his$girlCode) | duplicated(susp_his$girlCode, fromLast=TRUE)

susp_dupes <-susp_his[susp_dupes, ]

#dim(susp_dupes)

susp_dupes <- susp_dupes %>%
    mutate("Match" = "Yes")


susp_his <- rbind(susp_unique, susp_dupes)

#dim(susp_his)


    
```


```{r counci_name_susp, echo=FALSE}
## Change council names to be consistent wiht how they displayed with the surveys
susp_his$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, susp_his$council)

susp_his$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, susp_his$council)

susp_his$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, susp_his$council)

susp_his$council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, susp_his$council)

susp_his$council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, susp_his$council)

susp_his$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, susp_his$council)

susp_his$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, susp_his$council)

susp_his$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, susp_his$council)

susp_his$council <-sub("Pandhandle Council", "Panhandle Council", fixed = TRUE, susp_his$council)


susp_his$council <-sub("Girl Scouts of Gulfcoast Florida",  "Gateway Council", fixed = TRUE, susp_his$council)

```


# Introduction

Matching attendance data set from the past two membership years. The number of students in the dataset is `r nrow(susp_his)` and the number of matched students acorss the two years is `r nrow(susp_dupes)`. 


```{r update_year_behavior, echo=FALSE}
susp_his$Year_Id <-sub("M2",  "14-15", fixed = TRUE, susp_his$Year_Id)

susp_his$Year_Id <-sub("M3",  "15-16", fixed = TRUE, susp_his$Year_Id)


```



```{r council_stauts_behavior, echo=FALSE, eval=TRUE}
council_status <- with(susp_his,table(council, Year_Id))

council_status <- addmargins(council_status)

pander(council_status)

```






# Successful Outcome

```{r susp_suc, echo=FALSE}

susp_suc <- function(){
     
     no_susp  <- filter(susp_his, baseline == 0, final ==0)
     dec_susp <- filter(susp_his, susp_diff < 0)
     suc      <- rbind(no_susp, dec_susp)
     
}

#susp_suc

no_sup <- susp_his %>%
    filter(baseline == 0, final == 0)
    

no_per <-nrow(no_sup)/nrow(susp_his)

no_per <- percent(no_per)

#no_per

decrease_susp <- susp_his %>%
    filter(susp_diff < 0)

#nrow(decrease_susp)
#nrow(no_sup)
#nrow(susp_his)

dec_per <- nrow(decrease_susp) / nrow(susp_his)

dec_per <- percent(dec_per)

tot_suc <- dec_per + no_per

#tot_suc

```

Over the course of two years `r (tot_suc)` students  have had a successful outcome and `r (no_per) ` never received a suspension. A successful outcome is never receiving a suspension and decreasing amount of suspensions. 

However, there is a segment of students approximately 8 percent that on average increased the number of suspesnions from baseline to final. 

```{r percent, echo=FALSE}

susp_suc_y <- function(x){
     no_susp_y  <- filter(susp_his, Year_Id == x, baseline == 0, final ==0)
     dec_susp_y <- filter(susp_his, Year_Id == x, susp_diff < 0)
     suc_y      <- rbind(no_susp_y, dec_susp_y)
     suc_y
     
    }









```



```{r bev_suc, echo=FALSE}
bev_suc <- susp_suc()

bev_suc <- bev_suc %>%
    mutate(Success = "TRUE")

#nrow(bev_suc)



```

```{r not_successful, echo=FALSE}
bev_not <- susp_his%>%
    filter( final !=0)%>%
    filter( susp_diff >=0)

#nrow(bev_not)

bev_not <- bev_not %>%
    mutate(Success = "FALSE")

```

```{r susp_his_binded, echo=FALSE}
susp_his1 <- rbind(bev_suc, bev_not)

#nrow(susp_his1)
```

### By Council
```{r susp_his2, echo=FALSE}
susp_his2 <- susp_his1 %>%
    group_by(council)%>%
    count(Success)%>%
    mutate(percent = n /sum(n))

susp_his2$percent <- percent(susp_his2$percent)

susp_his2 <- susp_his2 %>%
    filter(Success == "TRUE")

kable(susp_his2)
```

### By Match

```{r susp_m, echo=FALSE}
susp_his1_m <- susp_his1 %>%
    group_by(Match)%>%
    count(Success)%>%
    mutate(percent = n /sum(n))

susp_his1_m$percent <- percent(susp_his1_m$percent)

susp_his1_m <- susp_his1_m %>%
    filter(Success == "TRUE")

kable(susp_his1_m)
```




```{r all, echo=FALSE, eval=FALSE}
all <- susp_suc()

all <- table(all$council)

all <- as.data.frame(all)


susp_his_c <- table(susp_his$council)

susp_his_c <- as.data.frame(susp_his_c)

#susp_his_c

all <- all %>%
    rename(council = Var1)%>%
    rename(success = Freq)

all_per <-cbind(susp_his_c, all)

all_per <- all_per%>%
    mutate(percent = success /Freq)

all_per$percent <- percent(all_per$percent)

all_per <- all_per %>%
    select(3,4,5)

kable(all_per)



```




```{r m2, echo=FALSE, eval=FALSE}
m2 <- susp_suc_y("14-15")

m2 <- table(m2$council)

m2 <- as.data.frame(m2)



#head(susp_his)

m2_all <- susp_his %>%
    filter(Year_Id == "M2")


m2_all_tbl <- table(m2_all$council)

m2_all_tbl <- as.data.frame(m2_all_tbl)

#m2_all_tbl

m2 <- m2 %>%
    rename(council = Var1)%>%
    rename(success = Freq)

m2_per <-cbind(m2_all_tbl, m2)

m2_per <- m2_per%>%
    mutate(percent = success /Freq)

m2_per$percent <- percent(m2_per$percent)

m2_per <- m2_per %>%
    select(3,4,5)

kable(m2_per)

```


```{r m3, echo=FALSE, eval=FALSE}

m3 <- susp_suc_y("15-16")

m3 <- table(m3$council)

m3 <- as.data.frame(m3)

#m3

m3_all <- susp_his %>%
    filter(Year_Id == "M3")


m3_all_tbl <- table(m3_all$council)

m3_all_tbl <- as.data.frame(m3_all_tbl)

#m3_all_tbl

m3 <- m3 %>%
    rename(council = Var1)%>%
    rename(success = Freq)

m3_per <-cbind(m3_all_tbl, m3)

m3_per <- m3_per%>%
    mutate(percent = success /Freq)

m3_per$percent <- percent(m3_per$percent)

m3_per <- m3_per %>%
    select(3,4,5)

kable(m3_per)


```

# Average Difference by Year

```{r susp_avg_y, echo=FALSE}
susp_avg_y <- susp_his %>%
    filter(baseline != 0, final !=0) %>%
    group_by(Year_Id)%>%
    summarise(avg_diff =mean(susp_diff) )

kable(susp_avg_y)
```


```{r susp_avg, echo=FALSE}
susp_avg_c <- susp_his %>%
    filter(baseline != 0, final !=0) %>%
    group_by(council, Year_Id)%>%
    summarise(avg_diff =mean(susp_diff) )

kable(susp_avg_c)
```

```{r susp_avg_cm, echo=FALSE, eval=FALSE}

susp_avg_cm <- susp_his %>%
    count(Match)

kable(susp_avg_cm)

```




```{r susp_avg_m, echo=FALSE, eval=TRUE}
susp_avg_m <- susp_his %>%
    filter(baseline != 0, final !=0) %>%
    group_by(Match)%>%
    summarise(avg_diff =mean(susp_diff) )
    
kable(susp_avg_m)

```


# Plots

```{r plots, echo=FALSE, fig.path='Figs/'}


susp_plot <- ggplot(susp_his,(aes(x =susp_diff, y =council)))
susp_plot + geom_count() + labs(x="Difference in Suspensions", title="Suspensions: Difference between baseline and final")

susp_plot_m <- ggplot(susp_his, (aes(x =susp_diff, y =Match)))
susp_plot_m + geom_count() + labs(x="Difference in Suspensions", title="Suspensions: Difference by Match")

susp_plot_m <- ggplot(susp_his, (aes(x =susp_diff, y = Year_Id)))
susp_plot_m + geom_count() + labs(x="Difference in Suspensions", title="Suspensions: Difference by Membership Year", y="Membership Year")



```





```{r no_sup, echo=FALSE, eval=FALSE}

no_susp_c <- susp_his %>%
    filter(baseline ==0 & final == 0)%>%
    count(council) 


kable(no_susp_c)



no_susp_y <- susp_his %>%
    filter(baseline ==0 & final == 0)%>%
    count(Year_Id, council)

kable(no_susp_y)



no_susp_m <- susp_his %>%
    filter(baseline ==0 & final == 0)%>%
    count(Match, council)

kable(no_susp_m)

#table(no_susp_m)


```



```{r decrease_susp, echo=FALSE, eval=FALSE}
decrease_susp_c <- susp_his %>%
    filter(susp_diff < 0)%>%
    count(council)

kable(decrease_susp_c)

decrease_susp_y <- susp_his %>%
    filter(susp_diff < 0)%>%
    count(Year_Id, council)

kable(decrease_susp_y)


decrease_susp_m <- susp_his %>%
    filter(susp_diff < 0)%>%
    count(Match, council)

kable(decrease_susp_m)


```







