---
title: "language_arts_history"
author: "Kevin Gilds, MPA"
date: "September 24, 2016"
output: html_document
---


```{r lang_dbase, echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite") 

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite") #established connection with database

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)

```

```{r lang_1516, echo=FALSE}
lang_1516 <-dbReadTable(getReal_2016db, "langarts_1516") #read langarts1516 table

lang_1516 <- lang_1516 %>%
    select(council, 1:4,6) %>%  #select variables of interest
    mutate("Year_Id" = "M3")  # add new variable and name M3
    


```

```{r lang_1415, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data") #change working directory to find database

getReal_2015db<- dbConnect(SQLite(),   dbname="data_Final_GetReal_2014_2015.sqlite") #read database

lang_1415 <-dbReadTable(getReal_2015db, "langarts_final_matched") #read lang_1415



lang_1415 <- lang_1415%>% 
    select(girlCode,council.x, q4Grade, q1Grade, langDiff) %>% #select variables
    rename(council = council.x, final = q4Grade, baseline = q1Grade, Grade_Change =langDiff) %>%  #rename variable names to match rest of df
    mutate("Year_Id" = "M2") #add variable and name it M2. 

```



```{r lang_1314, echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Analyis_data")

getReal_2014db<- dbConnect(SQLite(), dbname="getReal.sqlite") #find database 

lang_1314 <-dbReadTable(getReal_2014db, "langArtsFinal") #Need langarts table 13_14



```

```{r three_14, echo=FALSE}
three_14 <- lang_1314[grep("^314", lang_1314$girlCode),] #find and subset council codes with 314



three_14 <- three_14 %>%
    mutate("council" = "Gulfcoast Council") %>% #add council variable and name it
    mutate("langdiff" = finish - start) #add vairable and name it to match other df

```



```{r three_13, echo=FALSE}

three_13 <- lang_1314[grep("^313", lang_1314$girlCode),] #find and subset girl codess with 313



three_13 <-three_13 %>% 
    mutate("council" = "Gateway Council") %>% #add council varialbe and name it
    mutate("langdiff" = finish- start) #add variable to find grade difference for comparison


```

```{r three_20, echo=FALSE}

three_20 <- lang_1314[grep("^320", lang_1314$girlCode),] #find girlcodes that start with 320 and subset them


three_20 <- three_20 %>%
    mutate("council" = "West Central Council") %>% #add council varialbe to summarize data and match other datasets
    mutate("langdiff" = finish - start) #add calculdated field to provide analyiss.


```


```{r three_21, echo=FALSE}
three_21 <- lang_1314[grep("^321", lang_1314$girlCode),] #find girlCode that starts with 321 and subset them


three_21 <- three_21 %>%
    mutate("council" = "Southeast Council") %>% #add council to match other data sets and 
    mutate("langdiff" = finish - start)#add calculated fied to mathch other datasets for analysis


```


```{r three_22, echo=FALSE}

three_22 <- lang_1314[grep("^322", lang_1314$girlCode),] #find girlCode records that start with 322 and subset theem


three_22 <- three_22 %>%
    mutate("council" = "Pandhandle Council") %>% #add variable council to summarize data and match other datasets
    mutate("langdiff" = finish - start) #add calculated field to match other datasets 
   

```


```{r the_binding, echo=FALSE}

gateway_gulf <- rbind(three_13, three_14) #bind council 313 and 314

wcf <- rbind(gateway_gulf, three_20) #bind council wcf with 313_314

southeast <- rbind(wcf, three_21)  #bind southeast, with 313, 314, and 320

lang_1314_a <- rbind(southeast, three_22) #bind southeast with 322)

dim(lang_1314_a)

lang_1314_a <- lang_1314_a %>%
    mutate("Year_Id" = "M1") %>% #add MY variable to remind what year this is
    rename(baseline = start, final = finish, Grade_Change = langdiff) # re-name variable to match other set and merge all togheter

```

```{r reorder_1516, echo=FALSE}
lang_1516 <- lang_1516[,c(2,1,6,3,4,5)] #reorder variables
#df2[,c(1,3,2,4)]



```



```{r reorder 1314, echo=FALSE}
lang_1314_a<-lang_1314_a[,c(1,4, 6,2,3,5)] #rearrange variables
#df2[,c(1,3,2,4)]



```

```{r reorder_1415}
lang_1415 <- lang_1415[,c(1,2,6, 4, 3, 5)] #reorder 1415

head(lang_1415)

```

```{r lang_history, echo=FALSE}

lang_1 <-rbind(lang_1314_a, lang_1415) #combine 1314 and 1415

lang_history <- rbind(lang_1, lang_1516) #combined 1415_1314 & 1516



```



```{r council_name_fix}
## Change council names to be consistent wiht how they displayed with the surveys
lang_history$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, lang_history$council)

lang_history$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, lang_history$council)

lang_history$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, lang_history$council)

lang_history$council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, lang_history$council)

lang_history$council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, lang_history$council)

lang_history$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, lang_history$council)

lang_history$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, lang_history$council)

lang_history$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, lang_history$council)

lang_history$council <-sub("Pandhandle Council", "Panhandle Council", fixed = TRUE, lang_history$council)


lang_history$council <-sub("Girl Scouts of Gulfcoast Florida Inc.",  "Gulfcoast Council", fixed = TRUE, lang_history$council)

```


```{r lang_history_filtered, echo=FALSE}
lang_history_filtered <- lang_history %>%
    filter(baseline !=4 | final != 4) #filter out all A's. Compare means

summary(lang_history_filtered$Grade_Change) #summarize filtered data


hist(lang_history_filtered$Grade_Change) #create historgram to look at distribution


```


```{r stat_test, echo=FALSE}

t.test(lang_history$baseline, lang_history$final)

cohen.d(lang_history$baseline, lang_history$final)

```


Tests with filtered data
```{r stat test filtered, echo=FALSE}

t.test(lang_history_filtered$baseline, lang_history_filtered$final)

cohen.d(lang_history_filtered$baseline, lang_history_filtered$final)

```


```{r council_lang_summary, echo=FALSE}

year_id_lang_summary <- lang_history %>%
    group_by(Year_Id) #groupd data by Year_Id



year_id_lang_summary <-summarise(year_id_lang_summary, Grade_Change =mean(Grade_Change)) #summarize Grade change by year id

pander(year_id_lang_summary) #review the data


```




```{r plot_council_lang_summary}

ggplot(year_id_lang_summary, aes(y=Grade_Change, x=Year_Id, group=2)) + geom_line() + geom_point()

```



```{r lang_summary_council, echo=FALSE }

council_lang_summary_c <- lang_history %>%
    group_by(council,Year_Id)


council_lang_summary_c <-summarise(council_lang_summary_c, Grade_Change =mean(Grade_Change)) #summarize council grade change


pander(council_lang_summary_c)  #print summary nicely

ggplot(council_lang_summary_c, aes(y=Grade_Change, x=Year_Id, colour=council, group=2)) + geom_line()  + geom_point()  #graphical summary
