---
title: "matched_survey_history"
author: "Kevin Gilds, MPA"
date: "September 1, 2016"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)

```


```{r read_databases}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

hr <-dbReadTable(getReal_2016db,"hr_history")

ae <-dbReadTable(getReal_2016db,"ae_history")

am <-dbReadTable(getReal_2016db,"am_history")


```


```{r}
## Change council names to be consistent wiht how they displayed with the surveys
hr$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, hr$council)

hr$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, hr$council)

hr$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, hr$council)

hr$council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, hr$council)

hr$council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, hr$council)

hr$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, hr$council)

hr$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, hr$council)

hr$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, hr$council)

hr$council <-sub("Girl Scouts of Gulfcoast Florida Inc.",  "Gulfcoast Council", fixed = TRUE, hr$council)

```

# Introduction

Matching survey data set from the past three membership years.

* M1 = MY: 2013-2014

* M2 = MY: 2014-2015

* M3 = MY: 2015-2016


# Data Entry Status 

```{r}
council_status <- with(hr,table(council, Year_Id))

pander(council_status)

```



# Life Skills Outcome

## Healthy Relationships Life Skills

### Post Surveys

```{r}

council_hr <- hr %>%
    group_by(council)

achieved_hr_post <- with(council_hr, table(council, Post >= 4.45))

achieved_hr_post <-prop.table(achieved_hr_post,1)

achieved_hr_post<-round(achieved_hr_post*100,2)



pander(achieved_hr_post)

```



#### Post survey by Year (by Counts)
```{r}


council_hr_test <-council_hr %>%
    group_by(council,Year_Id) %>%
    count(Post >=4.45)

datatable(council_hr_test)

```



### Post Survey HR Average Score

```{r}
hr_avg <- hr %>%
    group_by(Year_Id) %>%
    summarise(Post =mean(Post))

pander(hr_avg)

```

```{r}
ggplot(hr_avg, aes(y=Post, x=Year_Id, group=2)) + geom_line() + geom_point()


```


### Post Survey Average Score by Council

```{r council_hr_post_tbl}


head(council_hr)

council_hr_post <-summarise(council_hr, Post =mean(Post))

pander (council_hr_post)

```



### Pre Surveys
```{r}
achieved_hr <- with(council_hr, table(council, Pre >= 4.45))

achieved_hr

achieved_hr_p <-prop.table(achieved_hr,1)

achieved_hr_p<-round(achieved_hr_p*100,2)

pander(achieved_hr_p)
```



### General Information 

The mean difference between pre and post survey is `r pander(mean(hr$hr.diff))`

```{r}





hist(hr$hr.diff, col="red", freq=FALSE)
hr_dent <- density(hr$hr.diff)
lines(hr_dent)



```

QNorm test
```{r}

qqnorm(hr$hr.diff)
qqline(hr$hr.diff, col = 2)

```

Shapiro Test
```{r}
shapiro.test(hr$hr.diff)
```


T-Test

```{r}
t.test(hr$Pre, hr$Post)



cohen.d(hr$Pre, hr$Post)
```



```{r}
healthy_change_p <- ggplot(hr,(aes(x=hr.diff, y=council)))
healthy_change_p + geom_count() + geom_hline(yintercept = 4.45) + geom_vline(xintercept = 0, col="red") + labs(x="Pre and Post Difference", y="Pre Outcome Score", title="Healthy Releationship Survey Results")


```


```{r}
year_id_hr <- hr %>%
    group_by(Year_Id)

year_id_hr <- summarize(year_id_hr, hr.diff = mean(hr.diff))

pander(year_id_hr)

year_id_hr$Year_Id <- as.factor(year_id_hr$Year_Id)

summary(year_id_hr)



ggplot(year_id_hr, aes(y=hr.diff, x=Year_Id, group=2)) + geom_line()

```



### Average Difference between Pre and Post by Council

```{r}
council_hr <- hr %>%
    group_by(council)

council_hr_c <-summarise(council_hr, hr.diff =mean(hr.diff))

pander(council_hr_c)



```


### Avergage Difference between Pre and Post by Membership Year

```{r council_hr}
council_hr <- hr %>%
    group_by(council, Year_Id)

council_hr_diff <-summarise(council_hr, hr.diff =mean(hr.diff))

pander(council_hr_diff)

datatable(council_hr_diff)

```




### Pre Surveys

```{r}


```


```{r}
council_hr_pre <-summarise(council_hr, Pre =mean(Pre))


datatable(council_hr_pre)


```



