---
title: "reading_arts_history"
author: "Kevin Gilds, MPA"
date: "September 24, 2016"
output:
  github_document: default
  html_document: default
  html_notebook: default
---


```{r read_dbase, echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite") 

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite") #established connection with database

library(DT)
library(getREAL)
library(dplyr)
library(pander)
library(ggplot2)
library(effsize)
library(knitr)
library(catspec)
library(formattable)

```

```{r read_1516, echo=FALSE}
read_1516 <-dbReadTable(getReal_2016db, "reading_1516") #read readarts1516 table

read_1516 <- read_1516 %>%
    select(council, 1:4,6) %>%  #select variables of interest
    mutate("Year_Id" = "M3")  # add new variable and name M3
    
read_1516 <- read_1516 %>%
    rename(baseline = basline)

```

```{r read_1415, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data") #change working directory to find database

getReal_2015db<- dbConnect(SQLite(),   dbname="data_Final_GetReal_2014_2015.sqlite") #read database

read_1415 <-dbReadTable(getReal_2015db, "reading_final_matched") #read read_1415



read_1415 <- read_1415%>% 
    select(girlCode,council.x, Q4Grade, Q1Grade, readDiff) %>% #select variables
    rename(council = council.x, final = Q4Grade, baseline = Q1Grade, Grade_Change =readDiff) %>%  #rename variable names to match rest of df
    mutate("Year_Id" = "M2") #add variable and name it M2. 

```



```{r read_1314, echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Analyis_data")

getReal_2014db<- dbConnect(SQLite(), dbname="getReal.sqlite") #find database 

read_1314 <-dbReadTable(getReal_2014db, "readingFinal") #Need readarts table 13_14



```

```{r three_14, echo=FALSE}
three_14 <- read_1314[grep("^314", read_1314$girlCode),] #find and subset council codes with 314



three_14 <- three_14 %>%
    mutate("council" = "Gulfcoast Council") %>% #add council variable and name it
    mutate("readdiff" = finish - start) #add vairable and name it to match other df

```


```{r three_13, echo=FALSE}

three_13 <- read_1314[grep("^313", read_1314$girlCode),] #find and subset girl codess with 313



three_13 <-three_13 %>% 
    mutate("council" = "Gateway Council") %>% #add council varialbe and name it
    mutate("readdiff" = finish- start) #add variable to find grade difference for comparison


```




```{r three_20, echo=FALSE}

three_20 <- read_1314[grep("^320", read_1314$girlCode),] #find girlcodes that start with 320 and subset them


three_20 <- three_20 %>%
    mutate("council" = "West Central Council") %>% #add council varialbe to summarize data and match other datasets
    mutate("readdiff" = finish - start) #add calculdated field to provide analyiss.


```


```{r three_21, echo=FALSE}
three_21 <- read_1314[grep("^321", read_1314$girlCode),] #find girlCode that starts with 321 and subset them


three_21 <- three_21 %>%
    mutate("council" = "Southeast Council") %>% #add council to match other data sets and 
    mutate("readdiff" = finish - start)#add calculated fied to mathch other datasets for analysis


```


```{r three_22, echo=FALSE}

three_22 <- read_1314[grep("^322", read_1314$girlCode),] #find girlCode records that start with 322 and subset theem


three_22 <- three_22 %>%
    mutate("council" = "Pandhandle Council") %>% #add variable council to summarize data and match other datasets
    mutate("readdiff" = finish - start) #add calculated field to match other datasets 
   

```


```{r the_binding, echo=FALSE}

gateway_gulf <- rbind(three_13, three_14) #bind council 313 and 314

wcf <- rbind(gateway_gulf, three_20) #bind council wcf with 313_314

southeast <- rbind(wcf, three_21)  #bind southeast, with 313, 314, and 320

read_1314_a <- rbind(southeast, three_22) #bind southeast with 322)



read_1314_a <- read_1314_a %>%
    mutate("Year_Id" = "M1") %>% #add MY variable to remind what year this is
    rename(baseline = start, final = finish, Grade_Change = readdiff) # re-name variable to match other set and merge all togheter

```

```{r reorder_1516, echo=FALSE}


read_1516 <- read_1516[,c(2,1,6,4,3,5)] #reorder variables
#df2[,c(1,3,2,4)]

#read_1516 <- read_1516 %>%
    #rename(baseline=basline)

#names(read_1516)

```



```{r reorder 1314, echo=FALSE}
read_1314_a<-read_1314_a[,c(1,4, 6,2,3,5)] #rearrange variables
#df2[,c(1,3,2,4)]



```

```{r reorder_1415, echo=FALSE}
read_1415 <- read_1415[,c(1,2,6, 4, 3, 5)] #reorder 1415



```

```{r read_history, echo=FALSE}

#names(read_1314_a)

#names(read_1415)

#names(read_1516)

read_1 <-rbind(read_1314_a, read_1415) #combine 1314 and 1415

read_history <- rbind(read_1, read_1516) #combined 1415_1314 & 1516



```

```{r echo=FALSE}

#dim(read_history)

read_history_unique<- read_history[!(duplicated(read_history$girlCode) | duplicated(read_history$girlCode, fromLast = TRUE)), ] #find and subset uniquie students

#dim(read_history_unique)

read_history_unique <- read_history_unique %>%
    mutate("Match" = "No")

read_history_dupes <-duplicated(read_history$girlCode) | duplicated(read_history$girlCode, fromLast=TRUE) #find duplicated cases

read_history_dupes <- read_history[read_history_dupes, ] # subset dupes


read_history_dupes <- read_history_dupes %>%
    mutate("Match" = "Yes")






```

```{r echo=FALSE}
read_history <- rbind(read_history_dupes, read_history_unique)
```



```{r council_name_fix_read, echo=FALSE}
## Change council names to be consistent wiht how they displayed with the surveys
read_history$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, read_history$council)

read_history$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, read_history$council)

read_history$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, read_history$council)

read_history$council <-sub("Southeast Council, Inc", "Southeast Council", fixed=TRUE, read_history$council)

read_history$council <-sub("Southeast Council.", "Southeast Council", fixed=TRUE, read_history$council)

read_history$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, read_history$council)

read_history$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, read_history$council)

read_history$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, read_history$council)

read_history$council <-sub("Pandhandle Council", "Panhandle Council", fixed = TRUE, read_history$council)


read_history$council <-sub("Girl Scouts of Gulfcoast Florida Inc.",  "Gulfcoast Council", fixed = TRUE, read_history$council)

```




```{r read_success_h, echo=FALSE}

read_success_h <- function() {
    read_dat <- filter(read_history, final >=2, Grade_Change >=0)
    read_dat <- nrow(read_dat)/nrow(read_history)
    read_dat <- round(read_dat*100,2)
    pander(paste0(read_dat,"%", sep= ""))

}



```



```{r echo=FALSE, eval=FALSE}
council_test <- table(read_history$council)

council_test

```







```{r read_success_df, echo=FALSE}
read_success_df <- read_history %>%
    filter(final >=2, Grade_Change >=0)
    

```




```{r eval=FALSE, echo=FALSE}
read_increase_m <- read_history %>%
    group_by(council)%>%
    filter(final >= 2, Grade_Change >0) %>%
    count(Match) %>%
    mutate(Percent = n/sum(n))

kable(read_increase_m)
```


```{r read_increase, echo=FALSE, eval=TRUE}
read_increase <- read_history %>%
    filter(final >=2, Grade_Change >0)
    



```


```{r read_main, echo=FALSE}
read_main <- read_history %>%
    filter(final >=2, Grade_Change ==0) #No grade change but maintained at least C grade
    

#head(read_main)

#dim(read_main)

```



```{r fail_baseline, echo=FALSE}

fail_baseline <- read_history %>%
    filter(baseline <= 1)


```



```{r fail_to_pass, echo=FALSE}

fail_to_pass <- read_history %>%
    filter(baseline <=1, final >=2)

fail_to_pass_p <- nrow(fail_to_pass) /nrow(fail_baseline)

fail_to_pass_p <- round(fail_to_pass_p*100,2)
fail_to_pass_p <- pander(paste0(fail_to_pass_p,"%", sep= ""))





```

# General Outcome Achievement

The number of students that were matched from the past 3 Membership Years is **`r nrow(read_history)`**

The percent of students with a successful outcome is **`r read_success_h()`**

* The number of students who increased their grade or maintained at least a C grade is **`r nrow(read_success_df)`**

    * The number of students with a final grade of C and increased their grade is **`r nrow(read_increase)`**
    
    * The number of students who maintained at least a C grade is **`r nrow(read_main)`**


The percent of students who went from failing to passing is **`r fail_to_pass_p`**

*   The number of students who increased grade from failing to passing **`r nrow(fail_to_pass)`**

*   The number of students who started with a failing grade but finihsed with a passing grade is **`r nrow (fail_baseline)`**


### Achievement by Council

```{r echo=FALSE}



read_success_s <- read_history %>%
    filter(final >=2, Grade_Change >=0)%>%
    mutate("Success" = "TRUE")

read_success_n <- read_history %>%
    filter(final >=2, Grade_Change  < 0) %>%
    mutate("Success" = "FALSE")

#nrow(read_success_n)

read_success_x <- read_history %>%
    filter(final < 2) %>%
    mutate("Success" = "FALSE")


read_success_1 <- rbind(read_success_s, read_success_n)

read_success_2 <- rbind(read_success_1, read_success_x)


#read_success_2


```



```{r eval=TRUE, echo=FALSE}



read_success <- read_success_2 %>%
    group_by(council) %>%
    count(Success) %>%
    mutate(percent = n /sum(n))
    

read_success$percent <- percent(read_success$percent)




kable(read_success)


```


```{r read_increase_tbl, echo=FALSE, eval=FALSE}

read_increase_tbl <- read_history %>%
    group_by(council, Year_Id) %>%
    count(final >=2, Grade_Change >=0) %>%
    mutate(Percent = n /sum(n))
    
pander(read_increase_tbl)
```











```{r read_history_filtered, echo=FALSE}
read_history_filtered <- read_history %>%
    filter(baseline !=4 | final != 4) #filter out all A's. Compare means

summary(read_history_filtered$Grade_Change) #summarize filtered data


hist(read_history_filtered$Grade_Change) #create historgram to look at distribution


```


```{r stat_test, echo=FALSE}

pander(t.test(read_history$baseline, read_history$final))

cohen.d(read_history$baseline, read_history$final)

```


Tests with filtered data
```{r stat test filtered, echo=FALSE}

pander(t.test(read_history_filtered$baseline, read_history_filtered$final))

cohen.d(read_history_filtered$baseline, read_history_filtered$final)

```

```{r}
read_m <- read_history %>%
    group_by(Match) %>%
    summarise(Grade_Change = mean(Grade_Change))


read_m


```



```{r council_read_summary, echo=FALSE}

year_id_read_summary <- read_history %>%
    group_by(Year_Id) #groupd data by Year_Id



year_id_read_summary <-summarise(year_id_read_summary, Grade_Change =mean(Grade_Change)) #summarize Grade change by year id

pander(year_id_read_summary) #review the data


```




```{r plot_council_read_summary}

ggplot(year_id_read_summary, aes(y=Grade_Change, x=Year_Id, group=2)) + geom_line() + geom_point() + labs (title= "Average Grade Change by Year")

```



```{r read_summary_council, echo=FALSE }

council_read_summary_c <- read_history %>%
    group_by(council,Year_Id)


council_read_summary_c <-summarise(council_read_summary_c, Grade_Change =mean(Grade_Change)) #summarize council grade change


pander(council_read_summary_c)  #print summary nicely

ggplot(council_read_summary_c, aes(y=Grade_Change, x=Year_Id, colour=council, group=2))  + geom_point(size=3) + labs(title= "Average Grade Change by Year and Council")   #graphical summary

```





